---
title: "Comparative analysis of SVM core predictor genes against DEG & WGCNA"
author: "Emeline Favreau"
date: "2021/12/13"
output: html_document
---

Copyright 2021 Emeline Favreau, University College London.

# Objective of analysis

We obtained 127 predictor genes from SVM models: these genes are common to all six species ( *Ceratina australensis*, *C. calcarata*, *Megalopta genalis*, *Polistes canadensis*, *P. dominula*, *Liostenogaster flavolineata*). We want to qualify them: are they also differentially expressed between reproductives and non-reproductives? are they also significantly associated with reproductive status in WGCNA?

## Analysis steps:

-   Obtaining data
-   Aim 1: Overlap of orthogroups (SVM, DEGs, WGCNA)
-   Aim 2: Common GO Terms enriched in all three analyses (SVM, DEGs, WGCNA)

```{r load all the libraries, eval = TRUE, echo = FALSE, include = FALSE}
# get libraries
basic_libraries <- c("UpSetR",
                     "tidyverse", 
                     "scales",
                     "ggplot2")

for (lib in basic_libraries) {
        if (require(package = lib, character.only = TRUE)) {
                print("Successful")
        } else {
                print("Installing")
                install.packages(lib)
                library(lib, character.only = TRUE )
        }
}
```

```{r import data, eval = TRUE, echo = FALSE, include = FALSE}
# common predictor genes (SVM)
predictor_genes <- 
  read.csv("../04-SVM/result/species-normalised/regression-on-all/127_common_predictor_genes",
  sep = "", stringsAsFactors = FALSE)

# common caste-specific genes (DEG)
de_genes <- 
  read.csv("../dge-DESeq2/orthology-dependent/orthogroups3718_all6spp_together/all_DEGs.txt",
  sep = "", stringsAsFactors = FALSE, header = FALSE)

# common co-expressed genes (WGCNA)
wgcna_genes <- 
  read.csv("../WGCNA/orthology-dependent/consensusNetwork_orthogroups3718/minModuleSize10/orthogroupList_SigModule-SigTraitAssociated.txt",
  sep = "", stringsAsFactors = FALSE, header = FALSE)


##################################
# GO terms for 127 predictor genes (all categories)
predictor_go <- 
  read.csv("../svm/result/species-normalised/regression-on-all/topgo_result_all_species_all_categories",
  sep = "\t", stringsAsFactors = FALSE)

# GO terms for common caste-specific genes (DEG, BP only)
de_go <- 
  read.csv("../ortho-enrichment/resultOnScratch/topgo_result_consensus-degs_BP",
  sep = "\t", stringsAsFactors = FALSE)

# GO terms common co-expressed genes (WGCNA)
wgcna_go <- 
  read.csv("../WGCNA/result/module_size_10/all/topgo_result_BP",
  sep = "\t", stringsAsFactors = FALSE)


```

# Aim 1: Overlap of orthogroups (SVM, DEGs, WGCNA)

```{r aim 1 orthogroup overlap, eval = TRUE, echo = FALSE, include = TRUE}
# comparative analysis of orthogroups 
# common to all three
common_svm_degs_vec <- predictor_genes$predictor_gene[predictor_genes$predictor_gene %in% de_genes$V1]
common_svm_wgcna_vec <- predictor_genes$predictor_gene[predictor_genes$predictor_gene %in% wgcna_genes$V1]
common_svm_degs_vec[common_svm_degs_vec %in% wgcna_genes$V1]


# make a vector for each species with the OG-orthogroups that are DEGs and SVMs
OG_listInput <- list(
  predictor_genes = predictor_genes$predictor_gene,
                           
  de_genes = de_genes$V1,
                           
  wgcna_genes = wgcna_genes$V1)

# str(OG_listInput)

upset(fromList(OG_listInput),
      sets = c("predictor_genes",
                "de_genes",
                "wgcna_genes"),
      order.by = "degree", keep.order = TRUE)

# keep a copy as pdf
pdf("DEGs_SVM_WGCNA_comparative_plot.pdf")
# plot comparative analysis of species DEGs in SVM core genes
upset(fromList(OG_listInput),
      sets = c("predictor_genes",
                "de_genes",
                "wgcna_genes"),
      order.by = "degree", keep.order = TRUE)# 
dev.off()
```

There is little overlap between the three genes sets. Two genes are common to all three: "OG0000706" (uncharacterized protein LOC408365 isoform X2 [Apis mellifera]) and "OG0001935" (uncharacterized protein LOC408661 isoform X1 [Apis mellifera]).

# Aim 2: Common GO Terms enriched in all three analyses (SVM, DEGs, WGCNA)

```{r aim 2 GO terms, eval = TRUE, echo = FALSE, include = TRUE}
# comparative analysis of GO Terms (BP)
predictor_go_BP_vec <- predictor_go$GO.ID[predictor_go$goCategory == "BP"]
de_go_BP_vec <- de_go$GO.ID[de_go$goCategory == "BP"]
wgcna_go_BP_vec <- wgcna_go$GO.ID[wgcna_go$goCategory == "BP"]

# common to all three: 15396
commongo_svm_degs_vec <- predictor_go_BP_vec[predictor_go_BP_vec %in% de_go_BP_vec]
commongo_svm_wgcna_vec <- predictor_go_BP_vec[predictor_go_BP_vec %in% wgcna_go_BP_vec]
commongo_svm_wgcna_deg_vec <- commongo_svm_degs_vec[commongo_svm_degs_vec %in% wgcna_go_BP_vec]

# vector of all possible GO terms (4226)
all_go_vec <- unique(c(predictor_go_BP_vec, de_go_BP_vec, wgcna_go_BP_vec))

# vector of Go terms common to all (2657)
common_go_vec <- c()

for(this_go in all_go_vec){
  if(this_go %in% predictor_go_BP_vec){
    if(this_go %in% de_go_BP_vec){
      if(this_go %in% wgcna_go_BP_vec){
  
        common_go_vec <- c(common_go_vec, this_go)
      }
    }
  }
}


# make a vector for each category
GO_listInput <- list(
  predictor_GO = predictor_go_BP_vec,
                           
  de_GO = de_go_BP_vec,
                           
  wgcna_GO = wgcna_go_BP_vec)

# str(GO_listInput)

upset(fromList(GO_listInput),
      sets = c("predictor_GO",
                "de_GO",
                "wgcna_GO"),
      order.by = "degree", keep.order = TRUE)

# keep a copy as pdf
pdf("DEGs_SVM_WGCNA_GO_comparative_plot.pdf")
# plot comparative analysis of species DEGs in SVM core genes
upset(fromList(GO_listInput),
      sets = c("predictor_GO",
                "de_GO",
                "wgcna_GO"),
      order.by = "degree", keep.order = TRUE)
dev.off()




#######
# REVIGO will reduce the GO terms for us, prvided we give a list of 2000 GO IDs
# Here we select the 2000 GO terms that have the lowest cumulative pvalue from the three analyses

# selecting the threshold for including GO terms into REVIGO analysis
svm_mean <- mean(predictor_go$pvalue[predictor_go$goCategory == "BP"])
deg_mean <- mean(de_go$pvalue[de_go$goCategory == "BP"])
wgcna_mean <- mean(wgcna_go$pvalue[wgcna_go$goCategory == "BP"])

# lowest cumulative p-value
common_go_pvalue_df <- data.frame(go = common_go_vec,
                                  svm_pvalue = NA,
                                  deg_pvalue = NA,
                                  wgcna_pvalue = NA,
                                  cumulative_pvalue = NA)


for(i in 1:length(common_go_vec)){
  # select pvalue from svm (mean of the six analyses)
  this_svm_mean <- mean(predictor_go$pvalue[predictor_go$goCategory == "BP" &
                     predictor_go$GO.ID == common_go_vec[i]])
  
  # select pvalue from DEGs (consensus, only one value)
  this_deg_mean <- mean(de_go$pvalue[de_go$goCategory == "BP" &
                      de_go$GO.ID == common_go_vec[i]])
  
  # select pvalue from WGCNAs (consensus, only one value)
  this_wgcna_mean <- mean(wgcna_go$pvalue[wgcna_go$goCategory == "BP" &
                        wgcna_go$GO.ID == common_go_vec[i]])
  
  this_cumulative_pvalue <- sum(this_svm_mean, this_wgcna_mean, this_deg_mean)
  # add result to table
  common_go_pvalue_df[i, 2:5] <- c(this_svm_mean, this_deg_mean,
                               this_wgcna_mean, this_cumulative_pvalue)
}

# check result
summary(common_go_pvalue_df$cumulative_pvalue)

# select the 2000 GO terms (max needed by REVIGO) whose cumulative pvalue is lowest
common_go_pvalue_ordered <- 
  common_go_pvalue_df[order(common_go_pvalue_df$cumulative_pvalue), ]

# select 2000 tops 
common_go_for_revigo <- common_go_pvalue_ordered$go[1:2000]

# save list of GO terms, as an input to REVIGO
write.table(common_go_for_revigo,
            file = "common_GO_terms_svm_deg_wgcna",
            row.names = FALSE,
            quote = FALSE,
            col.names = FALSE)


```

# Aim 3: Plot REVIGO result

```{r prepare REVIGO, eval = TRUE, echo = FALSE, include = TRUE}
# A plotting R script produced by the Revigo server at http://revigo.irb.hr/
# If you found Revigo useful in your work, please cite the following reference:
# Supek F et al. "REVIGO summarizes and visualizes long lists of Gene Ontology
# terms" PLoS ONE 2011. doi:10.1371/journal.pone.0021800


# load data needed, produced in svm/R-scripts/2021-12-10-svm-result-analysis.Rmd
gene2go <- readRDS("../svm/input/species-normalised/gene2go_for_revigo_fig.rds")
raw_selectionGenes <- readRDS("../svm/input/species-normalised/raw_selectionGenes_for_revigo_fig.rds")
myTable <- readRDS("../svm/input/species-normalised/myTable_for_revigo_fig.rds")
PredictorGenes <- readRDS("../svm/input/species-normalised/PredictorGenes_for_revigo_fig.rds")



# Here is your data from Revigo. 

revigo.names <- c("term_ID","description","frequency","plot_X","plot_Y","log_size","uniqueness","dispensability");
revigo.data <- rbind(c("GO:0000003","reproduction",12.5434631432545,4.15608157807236,-6.92930032022069,3.15956719323362,1,0),
c("GO:0002376","immune system process",2.86856745479833,4.04300670002925,-7.01584326747815,2.51982799377572,1,0),
c("GO:0003013","circulatory system process",0.147774687065369,3.92496156433555,-0.758060221366243,1.25527250510331,0.942509786634705,0),
c("GO:0007338","single fertilization",0.286856745479833,4.65844225821503,1.93111188668455,1.53147891704226,0.968349373587974,0),
c("GO:0007610","behavior",4.63317107093185,3.0622599784887,2.80279532165853,2.72754125702856,1,0),
c("GO:0007623","circadian rhythm",0.791029207232267,2.39262488580562,2.53127066560381,1.96378782734556,0.996415183690433,0),
c("GO:0007626","locomotory behavior",1.5125173852573,4.83867600945813,-6.0211391493091,2.24303804868629,0.98509523797108,0),
c("GO:0008150","biological_process",100,2.88282099263762,2.16286984410515,4.06088662300466,1,0),
c("GO:0008152","metabolic process",41.6376912378303,2.31711851992124,1.69662290219919,3.68042617085815,1,0),
c("GO:0009629","response to gravity",0.217315716272601,-7.02871116433285,0.0556278720565198,1.41497334797082,0.957042301062739,0),
c("GO:0009987","cellular process",67.9502781641168,1.57810004858862,-0.715385336963196,3.89309566609623,1,0),
c("GO:0016032","viral process",0.269471488178025,4.27803253490822,-6.83346699498094,1.50514997831991,1,0),
c("GO:0019674","NAD metabolic process",0.104311543810848,3.88120503971606,6.97058443779442,1.11394335230684,0.964913003393772,0),
c("GO:0022610","biological adhesion",1.7298331015299,2.22328220633059,-2.79634032420769,2.30102999566398,1,0),
c("GO:0023052","signaling",12.3609179415855,1.30407283019426,-0.863028289037839,3.15320490008428,1,0),
c("GO:0032501","multicellular organismal process",30.7892906815021,2.89957039546118,-4.24308897634828,3.54937115233318,1,0),
c("GO:0032502","developmental process",24.6696801112656,1.97494395516767,-2.15091691322127,3.45316539252586,1,0),
c("GO:0035010","encapsulation of foreign target",0.356397774687065,4.49905002816946,-6.48180010207344,1.6232492903979,0.983507040458755,0),
c("GO:0040007","growth",1.53859527121001,1.37141969112253,0.483876696963526,2.25042000230889,1,0),
c("GO:0040011","locomotion",5.53720445062587,1.21054148259444,0.851952016462101,2.80482067872116,1,0),
c("GO:0042908","xenobiotic transport",0.0608484005563282,-4.69201657830274,2.82531760753724,0.903089986991944,0.959769825338263,0),
c("GO:0043473","pigmentation",0.634561891515994,0.758718997629824,-0.178404230342379,1.86923171973098,1,0),
c("GO:0043903","regulation of biological process involved in symbiotic interaction",0.0521557719054242,1.38686749651002,-2.36629267889748,0.845098040014257,0.937532546389812,0),
c("GO:0044419","biological process involved in interspecies interaction between organisms",3.77260083449235,0.959739195677579,1.60468172871737,2.63848925695464,1,0),
c("GO:0046718","viral entry into host cell",0.217315716272601,-2.78223927744588,0.909952486821153,1.41497334797082,0.98911999088192,0),
c("GO:0048066","developmental pigmentation",0.556328233657858,0.678184641302624,0.379824718182507,1.81291335664286,0.991875691574822,0),
c("GO:0048511","rhythmic process",0.964881780250348,0.742164290102944,1.21296981455972,2.04921802267018,1,0),
c("GO:0050896","response to stimulus",23.5396383866481,0.203597918787825,0.121192101471406,3.43280900503317,1,0),
c("GO:0051179","localization",21.2621696801113,0.324522083632949,0.769384537792167,3.38863396935179,1,0),
c("GO:0065007","biological regulation",41.4551460361613,-0.0379955780210445,1.22861516017458,3.67851837904011,1,0),
c("GO:0098727","maintenance of cell number",0.886648122392211,6.80011864010439,-0.0742567252767474,2.01283722470517,0.919638614964242,0),
c("GO:0140253","cell-cell fusion",0.278164116828929,-1.00330568947106,0.904598398497577,1.51851393987789,0.978928827056164,0),
c("GO:0070997","neuron death",0.0173852573018081,-1.21590351025828,1.34019569703704,0.477121254719662,0.977350107466512,0.01703178),
c("GO:0072089","stem cell proliferation",0.0782336578581363,-0.359907614477643,0.914358916925099,1,0.977119416910853,0.01899659),
c("GO:0043063","intercellular bridge organization",0.13038942976356,6.47605963574367,3.73495026591439,1.20411998265592,0.943119061242934,0.01977122),
c("GO:0033301","cell cycle comprising mitosis without cytokinesis",0.173852573018081,2.52356158940564,0.837885368136694,1.32221929473392,0.953446674113729,0.02023594),
c("GO:0045197","establishment or maintenance of epithelial cell apical/basal polarity",0.226008344923505,-0.968092782926673,1.39319991073864,1.43136376415899,0.975111977889389,0.02067922),
c("GO:0022406","membrane docking",0.40855354659249,3.86893347147906,-5.35285797954836,1.68124123737559,0.978168126472951,0.02175459),
c("GO:0030048","actin filament-based movement",0.330319888734353,2.41513483207788,3.23116388343015,1.5910646070265,0.95703160574198,0.022088),
c("GO:0017145","stem cell division",0.40855354659249,4.71852150908545,-6.39766118178299,1.68124123737559,0.97242349146393,0.0225148),
c("GO:0061077","chaperone-mediated protein folding",0.425938803894298,-0.228236819042967,0.499995738591251,1.69897000433602,0.978082285539787,0.02260041),
c("GO:0008037","cell recognition",1.02573018080668,1.57917631641501,1.50831257231642,2.07554696139253,0.976096510539239,0.02467291),
c("GO:0016049","cell growth",0.643254520166898,4.89681523213214,-6.44574382452445,1.8750612633917,0.969141603800511,0.02572953),
c("GO:0008283","cell population proliferation",1.0778859527121,1.78635130690232,1.12634252892202,2.09691001300806,0.97597341194199,0.0271875),
c("GO:0061919","process utilizing autophagic mechanism",1.086578581363,-0.758513572462537,0.514422107517468,2.10037054511756,0.975953354017488,0.02736059),
c("GO:0006457","protein folding",1.13004172461752,4.46837168629442,-6.80208185828749,2.11727129565576,0.975854917515737,0.02750416),
c("GO:0007163","establishment or maintenance of cell polarity",1.69506258692629,1.9065319380421,2.46371148651884,2.29225607135648,0.974786654582156,0.02893292),
c("GO:0007155","cell adhesion",1.66029207232267,2.8094416234974,3.15646194978503,2.28330122870355,0.967178795470317,0.03029448),
c("GO:0008219","cell death",1.73852573018081,2.14074292967549,1.95236234562314,2.30319605742049,0.974716722507519,0.03046606),
c("GO:0030029","actin filament-based process",2.38178025034771,1.35691289168927,-0.300731469796857,2.43933269383026,0.97381263024123,0.03179637),
c("GO:0007017","microtubule-based process",3.99860917941586,1.41302023656628,1.97477645552707,2.66370092538965,0.972170186122079,0.03560336),
c("GO:0007267","cell-cell signaling",2.91203059805285,-3.76518235893708,-0.431470897821577,2.52633927738984,0.947048026799733,0.03666269),
c("GO:0007049","cell cycle",5.75452016689847,2.79469314590764,2.45422793348565,2.82151352840477,0.97088243921189,0.04077375),
c("GO:0006928","movement of cell or subcellular component",5.96314325452017,1.20535414747875,-0.00478698471436106,2.83695673705955,0.970749794486095,0.04364528),
c("GO:0007154","cell communication",12.9346314325452,3.16762819674896,3.18793924886481,3.17289469775218,0.967518345484006,0.05091157),
c("GO:0071840","cellular component organization or biogenesis",24.9826147426982,-0.225527430657174,1.62365083167206,3.45863784902565,0.964115807229507,0.07216148),
c("GO:0097164","ammonium ion metabolic process",0.0782336578581363,1.97501835090812,4.36196333490557,1,0.957156078964616,0.07295216),
c("GO:1905330","regulation of morphogenesis of an epithelium",0.00869262865090403,-2.12660344191866,-0.530797363479893,0.301029995663981,0.924432688144338,0.07363075),
c("GO:0051098","regulation of binding",0.243393602225313,1.21383054931679,-2.49031035780552,1.46239799789896,0.926576560456448,0.07594077),
c("GO:0098693","regulation of synaptic vesicle cycle",0.0173852573018081,-0.404723195242557,-1.31564784790137,0.477121254719662,0.920191635318387,0.07677807),
c("GO:0097502","mannosylation",0.208623087621697,0.16717221911485,2.45255432533843,1.39794000867204,0.959994708273569,0.07844027),
c("GO:2001023","regulation of response to drug",0.0260778859527121,-2.25112934726335,-1.55916425063781,0.602059991327962,0.925289622536792,0.07874706),
c("GO:0043094","cellular metabolic compound salvage",0.13038942976356,3.17156400538885,6.51694426277327,1.20411998265592,0.943279385940338,0.07980615),
c("GO:1901570","fatty acid derivative biosynthetic process",0.182545201668985,-0.728732161279403,3.33695253283046,1.34242268082221,0.933521288492753,0.08195809),
c("GO:0050792","regulation of viral process",0.0869262865090403,1.02111771032098,-2.57653385938675,1.04139268515823,0.934932876440108,0.08523794),
c("GO:0060078","regulation of postsynaptic membrane potential",0.234700973574409,2.98925833908634,-5.51371001762199,1.44715803134222,0.918515106641383,0.08540173),
c("GO:0019748","secondary metabolic process",0.756258692628651,3.32937088813266,6.93926016620296,1.94448267215017,0.957818644430605,0.09249392),
c("GO:0048070","regulation of developmental pigmentation",0.217315716272601,2.62477773293397,-7.22692561609508,1.41497334797082,0.92883157246785,0.0944678),
c("GO:0072091","regulation of stem cell proliferation",0.104311543810848,-2.62507405283635,-1.10003163299435,1.11394335230684,0.924565088306267,0.09579298),
c("GO:1901568","fatty acid derivative metabolic process",0.321627260083449,0.698492145651956,3.13506145967726,1.57978359661681,0.957138615873792,0.09626246),
c("GO:2000242","negative regulation of reproductive process",0.121696801112656,-2.6596024821446,-1.38554882521078,1.17609125905568,0.912253530958912,0.09694276),
c("GO:1903578","regulation of ATP metabolic process",0.139082058414465,0.523047262396704,-7.03076641895556,1.23044892137827,0.913518546177405,0.09796129),
c("GO:0072350","tricarboxylic acid metabolic process",0.104311543810848,-0.386142685029236,3.93939600441084,1.11394335230684,0.910107883577002,0.09853326),
c("GO:0035542","regulation of SNARE complex assembly",0.0695410292072323,1.07218313914611,-7.21789068967649,0.954242509439325,0.901477874615314,0.09854062),
c("GO:1901071","glucosamine-containing compound metabolic process",0.286856745479833,2.47455677784641,6.15013330474503,1.53147891704226,0.939765608738256,0.09963534),
c("GO:0006122","mitochondrial electron transport, ubiquinol to cytochrome c",0.121696801112656,3.25950849341338,7.11498776819944,1.17609125905568,0.935407141644113,0.09967069),
c("GO:0046148","pigment biosynthetic process",0.608484005563282,1.62747017597173,3.76923364510562,1.85125834871908,0.952202002921404,0.10240824),
c("GO:0008016","regulation of heart contraction",0.243393602225313,1.58951800031705,-6.97232021607574,1.46239799789896,0.915411469457329,0.10247335),
c("GO:0033619","membrane protein proteolysis",0.104311543810848,0.720522335838151,6.14464443619639,1.11394335230684,0.940726012627223,0.10451528),
c("GO:0042440","pigment metabolic process",1.04311543810848,3.13763971733596,6.70138771231588,2.08278537031645,0.956377527004382,0.10825081),
c("GO:0051302","regulation of cell division",0.347705146036161,-5.20260576432733,-4.81966964466254,1.61278385671974,0.920987337003528,0.11120076),
c("GO:0070085","glycosylation",1.10396383866481,2.12875853528653,4.84354893182706,2.10720996964787,0.956112816359214,0.11276597),
c("GO:0046034","ATP metabolic process",1.10396383866481,2.3954199790898,5.25601584837208,2.10720996964787,0.956112816359214,0.11347535),
c("GO:0032465","regulation of cytokinesis",0.165159944367177,1.31062412147255,-7.36884511146966,1.30102999566398,0.909682606038697,0.11543528),
c("GO:1901615","organic hydroxy compound metabolic process",1.66029207232267,-4.12589963535416,5.76645473641655,2.28330122870355,0.949315142313831,0.11885719),
c("GO:0042752","regulation of circadian rhythm",0.825799721835883,0.424402004271784,-5.96509075590069,1.98227123303957,0.920243478542678,0.11904911),
c("GO:0022407","regulation of cell-cell adhesion",0.278164116828929,0.661828828503583,-7.25131794527061,1.51851393987789,0.919654889858633,0.120647),
c("GO:0006790","sulfur compound metabolic process",1.52990264255911,1.24340459746577,6.83871826917215,2.24797326636181,0.928165990399688,0.12354215),
c("GO:0016052","carbohydrate catabolic process",0.573713490959666,1.57883625374653,6.22007536793917,1.82607480270083,0.93398668631094,0.12475681),
c("GO:0030155","regulation of cell adhesion",0.460709318497914,-2.45546430553652,-6.95962936200705,1.73239375982297,0.918885803459802,0.12616001),
c("GO:1901214","regulation of neuron death",0.356397774687065,-4.37905914158114,-4.30895517792553,1.6232492903979,0.914191158818714,0.12644278),
c("GO:0002697","regulation of immune effector process",0.669332406119611,-1.510491173925,-7.382240170309,1.89209460269048,0.912309221784137,0.12700245),
c("GO:0006721","terpenoid metabolic process",0.191237830319889,2.4397437495042,7.01279370628517,1.36172783601759,0.927875392145943,0.12749632),
c("GO:0050795","regulation of behavior",0.843184979137691,-0.097685146241956,-5.10642945532546,1.99122607569249,0.920075736259492,0.13006603),
c("GO:0046939","nucleotide phosphorylation",0.295549374130737,-1.15739115811032,3.81746793571995,1.54406804435028,0.912389038167644,0.13304421),
c("GO:0040012","regulation of locomotion",1.04311543810848,-1.4420866129203,-7.21154087791091,2.08278537031645,0.918320183474439,0.13331974),
c("GO:0032886","regulation of microtubule-based process",0.634561891515994,-3.00922125498368,-6.60980195472003,1.86923171973098,0.916351457891991,0.13342958),
c("GO:0035383","thioester metabolic process",0.49547983310153,-0.158700718682354,3.94267056489141,1.76342799356294,0.93055486699826,0.14028993),
c("GO:0042303","molting cycle",0.747566063977747,5.97646145585326,-4.31088102278784,1.93951925261862,0.941587242465349,0.14286869),
c("GO:0032970","regulation of actin filament-based process",0.99095966620306,-4.55308945408121,-4.88570947851,2.06069784035361,0.912540405746834,0.14399315),
c("GO:0005975","carbohydrate metabolic process",2.21662030598053,1.37107660955803,6.91074416469938,2.40823996531185,0.944348085959228,0.14608154),
c("GO:0002682","regulation of immune system process",2.13838664812239,-4.2158355037636,-4.86923837319572,2.39269695325967,0.911763768271243,0.1480758),
c("GO:0140053","mitochondrial gene expression",1.0778859527121,-3.42677734815416,6.08993544344556,2.09691001300806,0.934301028789049,0.15136121),
c("GO:0022404","molting cycle process",0.286856745479833,5.65787442389339,-4.68879557155076,1.53147891704226,0.94539386678442,0.1516839),
c("GO:0065009","regulation of molecular function",5.94575799721836,-3.52528221214745,-4.60303646289505,2.83569057149243,0.915240784610205,0.15463455),
c("GO:0008053","mitochondrial fusion",0.0608484005563282,5.36404320054447,5.47236451393678,0.903089986991944,0.937790506003547,0.15770281),
c("GO:0043972","histone H3-K23 acetylation",0.00869262865090403,0.392797318340335,4.65897717992713,0.301029995663981,0.929865929169657,0.15782945),
c("GO:0006576","cellular biogenic amine metabolic process",0.243393602225313,-0.782914044632474,7.30207388304491,1.46239799789896,0.909507043517137,0.16193349),
c("GO:0006091","generation of precursor metabolites and energy",1.76460361613352,1.12601396812456,6.96602341805233,2.3096301674259,0.927030501613241,0.16197489),
c("GO:0042127","regulation of cell population proliferation",1.89499304589708,-3.76634710705794,-4.81991336821982,2.34044411484012,0.906313829513616,0.16235327),
c("GO:0072347","response to anesthetic",0.0782336578581363,-6.93954880434595,-0.162395934138495,1,0.954119675236422,0.16650416),
c("GO:1901135","carbohydrate derivative metabolic process",4.44193324061196,-3.40166380982107,5.70609789105427,2.70926996097583,0.94300935272247,0.16684605),
c("GO:0040008","regulation of growth",2.70340751043115,-2.60731087829545,-6.10785380863502,2.49415459401844,0.909380190653249,0.16698902),
c("GO:0009308","amine metabolic process",0.243393602225313,0.786721829772983,7.55105229985635,1.46239799789896,0.944166322585897,0.17333265),
c("GO:0043954","cellular component maintenance",0.217315716272601,6.35214368187805,3.80472206509672,1.41497334797082,0.943029646778898,0.17341838),
c("GO:0051260","protein homooligomerization",0.139082058414465,4.9362516197993,5.16551207392798,1.23044892137827,0.92943599239222,0.174299),
c("GO:0090130","tissue migration",1.2952016689847,5.94134555037116,-4.09190382720116,2.17609125905568,0.938174308539977,0.17642305),
c("GO:0044281","small molecule metabolic process",6.91933240611961,-3.67585590848442,5.71954461741092,2.90145832139611,0.945255414059464,0.1767868),
c("GO:0099172","presynapse organization",0.182545201668985,5.45175440350642,4.0224089477144,1.34242268082221,0.939613852329457,0.17810987),
c("GO:0006855","xenobiotic transmembrane transport",0.00869262865090403,-4.44082819036783,2.63893548620659,0.301029995663981,0.949112738786265,0.17867851),
c("GO:0010941","regulation of cell death",2.28616133518776,-3.10622257160249,-4.98605838629368,2.42160392686983,0.904337140532491,0.17987855),
c("GO:0099024","plasma membrane invagination",0.252086230876217,4.93945825519077,4.52204351669621,1.47712125471966,0.938213474163791,0.18285526),
c("GO:0060537","muscle tissue development",0.121696801112656,7.3352078015554,0.0527433356932292,1.17609125905568,0.916016688543202,0.18437205),
c("GO:0051189","prosthetic group metabolic process",0.0521557719054242,-3.66534415882224,6.24021269800387,0.845098040014257,0.928211366994648,0.18566598),
c("GO:0032879","regulation of localization",4.7374826147427,-2.63301209664572,-4.87570678586167,2.73719264270474,0.903095937243201,0.18693282),
c("GO:0036098","male germ-line stem cell population maintenance",0.147774687065369,6.16174951918589,-3.26803985992915,1.25527250510331,0.921448462843322,0.18755606),
c("GO:0006629","lipid metabolic process",4.78094575799722,0.86476112719503,6.37717145652058,2.74115159885178,0.938904716060665,0.1876836),
c("GO:0009855","determination of bilateral symmetry",0.156467315716273,7.0595463213207,-2.24904399614099,1.27875360095283,0.905082347299025,0.18851447),
c("GO:0044087","regulation of cellular component biogenesis",2.70340751043115,-3.21537595704599,-4.89891390352474,2.49415459401844,0.902497023314446,0.18852801),
c("GO:0031503","protein-containing complex localization",0.478094575799722,-4.63533134147837,2.58545151886047,1.7481880270062,0.958789715294653,0.19125886),
c("GO:0006575","cellular modified amino acid metabolic process",0.764951321279555,0.467111345053886,6.87579354404156,1.94939000664491,0.92086013362978,0.19155708),
c("GO:0010565","regulation of cellular ketone metabolic process",0.13038942976356,-0.339951399343321,-7.33152857669515,1.20411998265592,0.906259885742891,0.1918464),
c("GO:0051726","regulation of cell cycle",2.76425591098748,-3.18436844060939,-4.81514969059986,2.50379068305718,0.902247180829637,0.19350102),
c("GO:0043455","regulation of secondary metabolic process",0.165159944367177,0.277767132343772,-7.45132772862257,1.30102999566398,0.912227894085174,0.19533922),
c("GO:0048863","stem cell differentiation",0.243393602225313,6.85062203078709,0.30167515558403,1.46239799789896,0.897386988198227,0.19626708),
c("GO:2000278","regulation of DNA biosynthetic process",0.0608484005563282,0.154019145126137,-7.18036209135683,0.903089986991944,0.906175153517801,0.1971106),
c("GO:0015844","monoamine transport",0.0434631432545202,-6.26452899035486,3.49427185531185,0.778151250383644,0.95377512861265,0.19766574),
c("GO:0035209","pupal development",0.147774687065369,6.16869239536876,-2.79910598927688,1.25527250510331,0.903211983647038,0.19781589),
c("GO:0009056","catabolic process",8.59700973574409,1.09852815671056,5.56468575372927,2.99563519459755,0.943581047336285,0.19956645),
c("GO:0033750","ribosome localization",0.113004172461752,-6.19157129330977,2.83664315061929,1.14612803567824,0.932531582151017,0.20102063),
c("GO:0043062","extracellular structure organization",0.686717663421419,6.38007050524191,4.06282016264929,1.90308998699194,0.936635848588799,0.20204399),
c("GO:0006793","phosphorus metabolic process",7.70166898470097,-2.43420519852819,5.51989062515822,2.94792361983173,0.912664151972023,0.20382697),
c("GO:0051239","regulation of multicellular organismal process",5.00695410292072,-2.5908698309265,-4.79281931537937,2.76117581315573,0.90242673178793,0.20599459),
c("GO:0065008","regulation of biological quality",11.4568845618915,-3.28465184700045,-4.84946172178925,3.12024479554637,0.907408443669879,0.20666029),
c("GO:0016999","antibiotic metabolic process",8.92037552155772,0.817930946331705,5.24069999723669,3.01157044359728,0.943285319047283,0.20997456),
c("GO:0060033","anatomical structure regression",0.530250347705146,7.18638040395812,-0.533032156429845,1.79239168949825,0.90174423567998,0.21160339),
c("GO:0048864","stem cell development",0.00869262865090403,6.19989358561639,0.659919256120748,0.301029995663981,0.914437574911609,0.21283983),
c("GO:0050793","regulation of developmental process",5.78929068150209,-2.35022679022263,-4.81104132305077,2.82412583391655,0.900623829304566,0.21306273),
c("GO:0007525","somatic muscle development",0.669332406119611,7.22868334110044,-0.0528087555853098,1.89209460269048,0.911399962284304,0.21666797),
c("GO:0006109","regulation of carbohydrate metabolic process",0.278164116828929,-0.288095860092847,-7.28188848550379,1.51851393987789,0.905033449193753,0.21889332),
c("GO:0062012","regulation of small molecule metabolic process",0.399860917941586,-0.509894495761621,-7.13198520265538,1.67209785793572,0.904913152518309,0.22235168),
c("GO:0072348","sulfur compound transport",0.260778859527121,-4.92051132882361,2.72939960653094,1.49136169383427,0.954553232098179,0.22418775),
c("GO:0051606","detection of stimulus",2.46870653685675,-6.75729455435009,-1.422754266802,2.45484486000851,0.953443050367438,0.22495304),
c("GO:0009058","biosynthetic process",11.9784422809458,0.687091912431322,5.38587875145158,3.13956426617585,0.940799581888905,0.22531912),
c("GO:0043467","regulation of generation of precursor metabolites and energy",0.347705146036161,-1.33218982698271,-6.91342959538909,1.61278385671974,0.899705005771812,0.22678829),
c("GO:0003008","system process",5.91098748261474,5.16329278236137,-3.25276590968568,2.83314711191279,0.926211110077695,0.22726696),
c("GO:0043470","regulation of carbohydrate catabolic process",0.113004172461752,0.464538079752399,-7.49618029172063,1.14612803567824,0.903477850955794,0.22958798),
c("GO:0022411","cellular component disassembly",0.973574408901252,6.29768364221263,4.14644903249334,2.05307844348342,0.934397011829556,0.23044342),
c("GO:0023051","regulation of signaling",7.94506258692629,-2.03614293888735,-4.87835339655525,2.96142109406645,0.89644088161205,0.23134218),
c("GO:0051128","regulation of cellular component organization",6.00660639777469,-2.3105639994119,-4.9112035040212,2.84010609445676,0.892619906052047,0.23293715),
c("GO:0007031","peroxisome organization",0.217315716272601,5.79772517713142,5.06642495092429,1.41497334797082,0.934116218355898,0.23533205),
c("GO:0007568","aging",1.54728789986092,7.25261895413764,-0.250217462378964,2.25285303097989,0.914766779471793,0.23708174),
c("GO:0043687","post-translational protein modification",0.0869262865090403,-1.32458158596101,4.51375657849824,1.04139268515823,0.922882343085712,0.23964275),
c("GO:0072524","pyridine-containing compound metabolic process",0.13038942976356,-2.37027771181149,6.91215075622042,1.20411998265592,0.907843591942208,0.23976821),
c("GO:0070193","synaptonemal complex organization",0.104311543810848,4.93575806178358,4.89628744677761,1.11394335230684,0.932754034536238,0.24509138),
c("GO:0060322","head development",1.19958275382476,7.074758181023,-0.375870044564485,2.14301480025409,0.913198375465465,0.24542281),
c("GO:0048583","regulation of response to stimulus",8.57962447844228,-2.05059268773206,-4.83915066560557,2.99475694458763,0.895369209486309,0.2495856),
c("GO:0061320","pericardial nephrocyte differentiation",0.0869262865090403,5.62100779892825,-1.32012549106067,1.04139268515823,0.881143026795149,0.25034769),
c("GO:1901360","organic cyclic compound metabolic process",14.221140472879,-1.52339415469535,4.89065615675397,3.21404867941194,0.932999980146235,0.25112314),
c("GO:0042060","wound healing",0.634561891515994,-6.93672755310437,-1.39945553813487,1.86923171973098,0.952463460477286,0.25246624),
c("GO:0010256","endomembrane system organization",1.65159944367177,6.21999356442586,4.27346767580505,2.28103336724773,0.930682341126465,0.2535943),
c("GO:0021700","developmental maturation",1.64290681502086,7.21945336275793,-0.301774474784271,2.27875360095283,0.914205821843939,0.25474749),
c("GO:0019216","regulation of lipid metabolic process",0.425938803894298,-0.451667469014113,-7.01470324753291,1.69897000433602,0.901194604178689,0.25644369),
c("GO:2000765","regulation of cytoplasmic translation",0.0869262865090403,-0.207190747437806,-7.16074787337562,1.04139268515823,0.894261861135074,0.25746393),
c("GO:0045943","positive regulation of transcription by RNA polymerase I",0.0695410292072323,0.0397887768949083,-7.04086375734706,0.954242509439325,0.887091039309737,0.25986492),
c("GO:0010646","regulation of cell communication",7.94506258692629,-2.11352969601885,-4.96347455390585,2.96142109406645,0.888646319214078,0.26062543),
c("GO:0071496","cellular response to external stimulus",0.869262865090403,-6.33294146026812,-0.464192591149812,2.00432137378264,0.949305355400923,0.26187267),
c("GO:0040013","negative regulation of locomotion",0.156467315716273,1.92535451918222,-7.27801537163137,1.27875360095283,0.904700610240326,0.26191269),
c("GO:0061061","muscle structure development",1.76460361613352,7.10291670575966,-0.625729065470698,2.3096301674259,0.909498945317102,0.26212535),
c("GO:0008340","determination of adult lifespan",1.46036161335188,6.10998461068076,-2.42759365355928,2.22788670461367,0.891073630303926,0.268365),
c("GO:0042558","pteridine-containing compound metabolic process",0.182545201668985,-1.67228459518439,7.12763747232055,1.34242268082221,0.9063243190003,0.27143377),
c("GO:0097435","supramolecular fiber organization",1.79937413073713,5.85424134278082,4.11554579556264,2.31806333496276,0.930039217900297,0.27277416),
c("GO:0010467","gene expression",10.1877607788595,-1.16345345334719,5.27466024684498,3.06929801211553,0.924507781749789,0.27279268),
c("GO:0022616","DNA strand elongation",0.147774687065369,-2.21126184001112,6.754247876124,1.25527250510331,0.89607010846203,0.27408316),
c("GO:0051674","localization of cell",2.86856745479833,-5.20201360127033,3.22234880942205,2.51982799377572,0.92761405350083,0.27411427),
c("GO:0001655","urogenital system development",0.634561891515994,6.58621557217185,-2.18816647304704,1.86923171973098,0.887876681693935,0.27643628),
c("GO:0007033","vacuole organization",0.469401947148818,5.69447273786671,5.03339716789752,1.74036268949424,0.92938343699795,0.27716613),
c("GO:0009894","regulation of catabolic process",2.57301808066759,-1.03391739236897,-6.14543808921643,2.47275644931721,0.884515525321643,0.27813765),
c("GO:0048519","negative regulation of biological process",13.586578581363,-1.8275476457518,-4.91972012812149,3.19423674872383,0.888436500347595,0.27966524),
c("GO:0034330","cell junction organization",2.1644645340751,6.1433744735019,4.22587218826204,2.39794000867204,0.928610516298592,0.28217023),
c("GO:0051865","protein autoubiquitination",0.13038942976356,-3.185709107175,6.27461348799825,1.20411998265592,0.920033626369666,0.28704611),
c("GO:0072525","pyridine-containing compound biosynthetic process",0.104311543810848,-2.21520029733084,6.56570354147292,1.11394335230684,0.885371183114597,0.28741475),
c("GO:0072527","pyrimidine-containing compound metabolic process",0.278164116828929,-2.03802242467886,6.86543145691832,1.51851393987789,0.901646430529381,0.28830421),
c("GO:0006356","regulation of transcription by RNA polymerase I",0.0782336578581363,-0.0871869510013338,-7.39280081394244,1,0.904515669122216,0.29000431),
c("GO:0046483","heterocycle metabolic process",13.2041029207232,-1.66396904818239,5.36374759051753,3.18184358794477,0.905784364834833,0.29007688),
c("GO:0061024","membrane organization",2.3730876216968,5.97602505755215,4.12017086028152,2.43775056282039,0.927876384332264,0.29248073),
c("GO:0021551","central nervous system morphogenesis",0.121696801112656,7.06840622956641,-1.37492676331891,1.17609125905568,0.888941263554905,0.29660416),
c("GO:0042133","neurotransmitter metabolic process",0.104311543810848,-4.61265594038389,4.91057747145291,1.11394335230684,0.870643235984851,0.29695567),
c("GO:0009410","response to xenobiotic stimulus",0.156467315716273,-6.98951191170876,-0.27489082611134,1.27875360095283,0.951478688300239,0.30051803),
c("GO:0043491","protein kinase B signaling",0.0173852573018081,-6.3667193249696,-2.21985092792103,0.477121254719662,0.884809008065351,0.30051929),
c("GO:0034063","stress granule assembly",0.0695410292072323,5.15473341467233,5.35170403527818,0.954242509439325,0.92911415995606,0.30133308),
c("GO:0048284","organelle fusion",0.573713490959666,5.53681214738675,5.02803974675762,1.82607480270083,0.928034699597221,0.30273735),
c("GO:0060260","regulation of transcription initiation from RNA polymerase II promoter",0.147774687065369,-0.665041788009655,-7.18766279395005,1.25527250510331,0.898030906631833,0.30599478),
c("GO:0046847","filopodium assembly",0.0869262865090403,6.32545692350229,3.92382562194431,1.04139268515823,0.92912455891599,0.30626791),
c("GO:0006275","regulation of DNA replication",0.365090403337969,-1.35652450583137,-6.85419456062822,1.63346845557959,0.895038531912329,0.30675743),
c("GO:0044550","secondary metabolite biosynthetic process",0.286856745479833,0.602022366192636,3.93408524266496,1.53147891704226,0.931789801183161,0.30721902),
c("GO:0050688","regulation of defense response to virus",0.173852573018081,0.158332796265619,-5.73294055507975,1.32221929473392,0.907691990228269,0.30740763),
c("GO:0060250","germ-line stem-cell niche homeostasis",0.165159944367177,3.18497198497278,-5.67925635352013,1.30102999566398,0.913135972352573,0.30790702),
c("GO:0034612","response to tumor necrosis factor",0.113004172461752,-7.02126941796639,-0.349117063174195,1.14612803567824,0.944244729600086,0.30886104),
c("GO:0040003","chitin-based cuticle development",1.7298331015299,5.9518546077005,-2.3255671102116,2.30102999566398,0.888811102048507,0.30990263),
c("GO:0009628","response to abiotic stimulus",3.56397774687065,-6.790902181131,-1.42757789641674,2.61384182187607,0.951478157236231,0.31438988),
c("GO:0032940","secretion by cell",1.5125173852573,-5.49184861859287,3.53312547686892,2.24303804868629,0.917994577068477,0.31488834),
c("GO:0099515","actin filament-based transport",0.0869262865090403,-5.35125043123085,2.70485953922076,1.04139268515823,0.931298653749805,0.31638882),
c("GO:0006997","nucleus organization",0.764951321279555,5.75800950951207,4.87173102235808,1.94939000664491,0.926007304043562,0.31747165),
c("GO:0051052","regulation of DNA metabolic process",0.434631432545202,-1.28064892178036,-6.74427670915627,1.70757017609794,0.892255615879029,0.31763049),
c("GO:0090329","regulation of DNA-dependent DNA replication",0.252086230876217,-1.06263253378344,-7.03818450520621,1.47712125471966,0.897415478531709,0.32088598),
c("GO:2000142","regulation of DNA-templated transcription, initiation",0.147774687065369,-0.629971275096756,-7.10984657051446,1.25527250510331,0.899309433391268,0.32092513),
c("GO:0098739","import across plasma membrane",0.330319888734353,-5.15760229329837,2.92358708279063,1.5910646070265,0.932381734928982,0.32122016),
c("GO:0045478","fusome organization",0.13038942976356,5.91581641908424,2.46379811603309,1.20411998265592,0.877093706917946,0.32222715),
c("GO:0042335","cuticle development",2.03407510431154,5.9083270596418,-2.22627976111329,2.37106786227174,0.887707780848348,0.32281572),
c("GO:0048518","positive regulation of biological process",15.6119610570236,-1.76810235045999,-4.9630266618475,3.25454807710897,0.886145656207672,0.32311482),
c("GO:0015872","dopamine transport",0.0173852573018081,-6.12066616045643,3.76372126739809,0.477121254719662,0.948765658038112,0.32377395),
c("GO:0061458","reproductive system development",0.704102920723227,5.86837699049084,-2.12857670859588,1.91381385238372,0.886724996993373,0.32631695),
c("GO:0001101","response to acid chemical",0.234700973574409,-7.00419669401771,-0.477414445582755,1.44715803134222,0.949786759791642,0.32689925),
c("GO:0043933","protein-containing complex subunit organization",4.85048678720445,5.99579437310274,4.27614879133262,2.74741180788642,0.921599959525107,0.32735616),
c("GO:0048859","formation of anatomical boundary",0.382475660639778,7.18057670999484,-0.431059508807616,1.65321251377534,0.899148662256032,0.32803634),
c("GO:0034502","protein localization to chromosome",0.156467315716273,-6.06938398013361,2.83227830240999,1.27875360095283,0.928721207771761,0.33042891),
c("GO:0051174","regulation of phosphorus metabolic process",1.80806675938804,-1.49026733126975,-6.11754364655757,2.32014628611105,0.881513169663043,0.33054328),
c("GO:0006725","cellular aromatic compound metabolic process",13.6387343532684,-1.53888696178273,5.32131982760721,3.19589965240923,0.905333999051499,0.33134559),
c("GO:0071526","semaphorin-plexin signaling pathway",0.0608484005563282,-6.04212741802224,-2.22195134780422,0.903089986991944,0.87391439580106,0.33492969),
c("GO:0006807","nitrogen compound metabolic process",33.3275382475661,-1.93777296578406,5.12743621105674,3.583765368285,0.929961655012902,0.33539636),
c("GO:0006509","membrane protein ectodomain proteolysis",0.0782336578581363,0.893574935612583,7.50104230592427,1,0.942106787314286,0.33543682),
c("GO:0007507","heart development",0.834492350486787,6.45142051209847,-2.09237083906582,1.98677173426624,0.873782940743065,0.335491),
c("GO:0016050","vesicle organization",0.999652294853964,5.77966460194942,4.79109449043262,2.06445798922692,0.924014443816217,0.33606978),
c("GO:0043603","cellular amide metabolic process",4.45931849791377,-1.41330264503239,6.26440929326605,2.71096311899528,0.886529978097891,0.33748282),
c("GO:0001763","morphogenesis of a branching structure",0.521557719054242,7.04920536903214,-1.16159850020388,1.78532983501077,0.892787447939837,0.33773005),
c("GO:0031647","regulation of protein stability",0.504172461752434,3.08199893057952,-6.19032785408822,1.77085201164214,0.912642834715026,0.33819675),
c("GO:0045165","cell fate commitment",2.65125173852573,6.64020916402765,-0.367272401208999,2.48572142648158,0.869666724824722,0.33902783),
c("GO:0000380","alternative mRNA splicing, via spliceosome",0.0521557719054242,-2.14668014512559,7.16491117037276,0.845098040014257,0.90668549414191,0.33936972),
c("GO:0040036","regulation of fibroblast growth factor receptor signaling pathway",0.104311543810848,-2.92572727062285,-6.97982473784721,1.11394335230684,0.907455735291348,0.33964281),
c("GO:0072359","circulatory system development",0.843184979137691,5.98673143293902,-2.1835585410753,1.99122607569249,0.884670461390776,0.34181574),
c("GO:0015850","organic hydroxy compound transport",0.191237830319889,-5.66443620280502,3.83763070014285,1.36172783601759,0.949412107998427,0.34242336),
c("GO:0007187","G protein-coupled receptor signaling pathway, coupled to cyclic nucleotide second messenger",0.0782336578581363,-6.04511862321591,-2.37897700825051,1,0.873907715420514,0.34280399),
c("GO:0043631","RNA polyadenylation",0.191237830319889,-2.44479455107084,6.7364532190872,1.36172783601759,0.900571224381611,0.34285685),
c("GO:0015833","peptide transport",0.0434631432545202,-6.24106873455844,3.59639154776655,0.778151250383644,0.953287718857325,0.34293624),
c("GO:0015837","amine transport",0.0434631432545202,-6.25482092189243,3.54335767634167,0.778151250383644,0.95377512861265,0.34293624),
c("GO:0048736","appendage development",2.84248956884562,5.87856349119715,-1.99451634238378,2.51587384371168,0.883340287047137,0.34432006),
c("GO:1901617","organic hydroxy compound biosynthetic process",0.686717663421419,-3.87110840775886,5.77534079695358,1.90308998699194,0.920765905964691,0.34478657),
c("GO:0007530","sex determination",0.304242002781641,6.30211539124766,0.168808190920636,1.55630250076729,0.904028979001691,0.34566447),
c("GO:0030716","oocyte fate determination",0.295549374130737,6.87386791205951,0.225487934485077,1.54406804435028,0.887886653589636,0.34599025),
c("GO:0007164","establishment of tissue polarity",0.678025034770515,7.06222108188633,-0.527234916608987,1.89762709129044,0.899365720999533,0.34638885),
c("GO:0055123","digestive system development",0.964881780250348,6.06345168571781,-2.1643889235351,2.04921802267018,0.883083521602793,0.34708571),
c("GO:0042659","regulation of cell fate specification",0.226008344923505,-2.46890413159106,-2.92279068450793,1.43136376415899,0.90128217543416,0.34763302),
c("GO:0043543","protein acylation",0.982267037552156,-2.01508136253613,5.78004277988946,2.05690485133647,0.903939004493003,0.34883054),
c("GO:0035637","multicellular organismal signaling",0.0956189151599444,3.52184335080951,-3.69174970587281,1.07918124604762,0.932421795877133,0.34936244),
c("GO:0050821","protein stabilization",0.347705146036161,3.09667281324582,-5.84956254994508,1.61278385671974,0.915600129540161,0.35033434),
c("GO:1905268","negative regulation of chromatin organization",0.0434631432545202,-0.813154432328828,-3.889223342148,0.778151250383644,0.887039814152727,0.35216922),
c("GO:0035249","synaptic transmission, glutamatergic",0.104311543810848,-4.29919714097956,-0.719243596224649,1.11394335230684,0.957037103468214,0.35228485),
c("GO:0035272","exocrine system development",1.00834492350487,6.11333736489087,-2.22734267366321,2.06818586174616,0.882555200753672,0.35380664),
c("GO:0006508","proteolysis",7.80598052851182,-0.463821391996145,6.05732193220568,2.95375969173323,0.910361664720546,0.35680076),
c("GO:0034248","regulation of cellular amide metabolic process",2.42524339360223,-1.42002215671483,-5.97742741918431,2.44715803134222,0.875362208762288,0.35808936),
c("GO:0035150","regulation of tube size",0.460709318497914,3.13081718802981,-6.14019711332305,1.73239375982297,0.908802517816556,0.35957398),
c("GO:0007422","peripheral nervous system development",0.478094575799722,6.37880417996261,-2.35577543805106,1.7481880270062,0.883851751649067,0.35986253),
c("GO:0034754","cellular hormone metabolic process",0.478094575799722,-2.24827020562784,2.92711320551038,1.7481880270062,0.853912462502539,0.36082658),
c("GO:0019222","regulation of metabolic process",20.3494436717663,-1.74058656561462,-5.02654599821098,3.36958689073634,0.881488315897342,0.36095757),
c("GO:0042886","amide transport",0.104311543810848,-6.21363499927207,3.39382929059373,1.11394335230684,0.952650837084303,0.36349071),
c("GO:0045022","early endosome to late endosome transport",0.0608484005563282,-5.94121519258607,3.02939819444292,0.903089986991944,0.930108209252866,0.36669642),
c("GO:0000381","regulation of alternative mRNA splicing, via spliceosome",0.747566063977747,-1.3278808774268,-6.51590063873063,1.93951925261862,0.883068304110335,0.36745584),
c("GO:0014019","neuroblast development",0.173852573018081,6.35121302542897,-1.01805045612035,1.32221929473392,0.866298256843752,0.37083499),
c("GO:0009566","fertilization",0.304242002781641,4.79050903741224,1.96419093920049,1.55630250076729,0.968177498517563,0.37147376),
c("GO:0051271","negative regulation of cellular component movement",0.0956189151599444,-0.904160430598828,-2.91658861564509,1.07918124604762,0.889163828257476,0.37222466),
c("GO:0008544","epidermis development",0.530250347705146,7.31118493380344,-0.599179162319802,1.79239168949825,0.904171454005255,0.37306357),
c("GO:0051896","regulation of protein kinase B signaling",0.139082058414465,-4.38550577181318,-5.9007992530126,1.23044892137827,0.905004378240115,0.37322227),
c("GO:0007005","mitochondrion organization",1.99061196105702,5.68515588551045,4.7215762293247,2.36172783601759,0.918344444893926,0.37378427),
c("GO:0030030","cell projection organization",5.56328233657858,6.02794244305182,4.34064134166992,2.80685802951882,0.920266036704537,0.37450795),
c("GO:1900076","regulation of cellular response to insulin stimulus",0.373783031988873,-4.27297746992566,-5.6945936443216,1.64345267648619,0.902146453815973,0.37593593),
c("GO:0010035","response to inorganic substance",0.817107093184979,-6.8374996684524,-0.73226113267538,1.97772360528885,0.943744624799217,0.37664615),
c("GO:0022613","ribonucleoprotein complex biogenesis",2.72948539638387,6.0054046474702,4.50013996363345,2.4983105537896,0.918088952809028,0.37709651),
c("GO:0060047","heart contraction",0.0521557719054242,5.5132310910601,-5.0558033010605,0.845098040014257,0.946162360360039,0.37811696),
c("GO:0007552","metamorphosis",3.99860917941586,6.0507674822759,-1.76451994600668,2.66370092538965,0.878511664347669,0.37864714),
c("GO:0015868","purine ribonucleotide transport",0.0782336578581363,-6.12723169898811,3.64323671019618,1,0.948241130935399,0.37873135),
c("GO:0042391","regulation of membrane potential",0.791029207232267,2.78700904273279,-5.97188155915002,1.96378782734556,0.908762720659935,0.3787627),
c("GO:0009605","response to external stimulus",8.25799721835883,-6.6599273952964,-1.25470783208701,2.97818051693741,0.946281357062987,0.37952433),
c("GO:0010608","posttranscriptional regulation of gene expression",2.57301808066759,-0.939327903720557,-6.13700811353134,2.47275644931721,0.880206042138958,0.37980642),
c("GO:0002065","columnar/cuboidal epithelial cell differentiation",0.156467315716273,6.92754524204761,-0.030766956786148,1.27875360095283,0.883147724510562,0.38107716),
c("GO:0006261","DNA-dependent DNA replication",0.738873435326843,-2.43005813729818,5.65757260057474,1.93449845124357,0.886241528384156,0.38282448),
c("GO:0007424","open tracheal system development",2.06884561891516,6.17770014063103,-1.9883257849647,2.37839790094814,0.869442748256943,0.38564869),
c("GO:1901264","carbohydrate derivative transport",0.226008344923505,-5.11157445872713,2.97486792621948,1.43136376415899,0.948675150394029,0.38812852),
c("GO:0006730","one-carbon metabolic process",0.269471488178025,1.44579791968954,7.41948955575756,1.50514997831991,0.907389769693702,0.38899149),
c("GO:0000959","mitochondrial RNA metabolic process",0.269471488178025,-1.97908963078124,6.89523665663895,1.50514997831991,0.897561072981312,0.38909987),
c("GO:1901068","guanosine-containing compound metabolic process",0.00869262865090403,-0.618873803186404,7.33961526665034,0.301029995663981,0.891148709483686,0.39143361),
c("GO:0009888","tissue development",8.70132127955494,6.89949210308253,-0.839647586828119,3.00086772153123,0.889999972558807,0.39175547),
c("GO:0030522","intracellular receptor signaling pathway",0.321627260083449,-5.52178352348416,-2.6640425805964,1.57978359661681,0.85906670076465,0.3950493),
c("GO:0048332","mesoderm morphogenesis",0.252086230876217,7.28540726643304,-0.665774008550488,1.47712125471966,0.8947379983948,0.39727151),
c("GO:0007277","pole cell development",0.260778859527121,5.96873079108736,-0.356026229145195,1.49136169383427,0.866032734977747,0.39765302),
c("GO:0046661","male sex differentiation",0.260778859527121,5.63458401930638,-0.908721217972042,1.49136169383427,0.884475073889871,0.39765302),
c("GO:1902275","regulation of chromatin organization",0.252086230876217,-1.40604295047436,-4.66240627541209,1.47712125471966,0.89545072660605,0.39887632),
c("GO:0010001","glial cell differentiation",0.365090403337969,6.24901864487325,-1.15933233532725,1.63346845557959,0.860698921033387,0.39907786),
c("GO:0043405","regulation of MAP kinase activity",0.0695410292072323,0.529042262817789,-7.05935533323727,0.954242509439325,0.886184301572819,0.39952184),
c("GO:0098927","vesicle-mediated transport between endosomal compartments",0.0608484005563282,-4.72769509424096,2.60921363498459,0.903089986991944,0.93798256338292,0.39958675),
c("GO:0050975","sensory perception of touch",0.113004172461752,5.60665040808473,-4.85097662958593,1.14612803567824,0.942477513760119,0.40009411),
c("GO:0016073","snRNA metabolic process",0.269471488178025,-2.11484890604847,6.84780156332599,1.50514997831991,0.895742241294486,0.40037686),
c("GO:0042219","cellular modified amino acid catabolic process",0.113004172461752,-0.188958227914573,4.89808316659985,1.14612803567824,0.918670468339438,0.40065082),
c("GO:0000963","mitochondrial RNA processing",0.147774687065369,-2.01866758699267,7.01973880769146,1.25527250510331,0.899134127110357,0.40092964),
c("GO:0008277","regulation of G protein-coupled receptor signaling pathway",0.278164116828929,-4.04063497377476,-5.96996814520266,1.51851393987789,0.900804550625235,0.4025956),
c("GO:0007584","response to nutrient",0.139082058414465,-6.7489723418199,-0.219759884512954,1.23044892137827,0.944435644257479,0.40413426),
c("GO:0033036","macromolecule localization",8.36230876216968,-5.35984233568179,3.37184898410108,2.98362628712453,0.943278323396498,0.40414156),
c("GO:0010817","regulation of hormone levels",0.956189151599444,2.67526785299729,-5.96141830700044,2.04532297878666,0.907022277388223,0.40430891),
c("GO:0010038","response to metal ion",0.49547983310153,-6.9239708512739,-0.642682194067823,1.76342799356294,0.945878873423143,0.40447095),
c("GO:0019226","transmission of nerve impulse",0.0956189151599444,3.83380626587355,-3.91084120703448,1.07918124604762,0.90966452055218,0.40463525),
c("GO:0007389","pattern specification process",4.42454798331015,5.97320810677817,-1.94289208625506,2.70757017609794,0.87699941441073,0.40508564),
c("GO:0007300","ovarian nurse cell to oocyte transport",0.278164116828929,4.20801130522362,-0.230530412729987,1.51851393987789,0.826288600870885,0.40577047),
c("GO:0043484","regulation of RNA splicing",0.930111265646732,-1.33125297577712,-6.43593692766205,2.03342375548695,0.882687788304004,0.40583904),
c("GO:0042866","pyruvate biosynthetic process",0.00869262865090403,1.95770636410794,6.47109861551194,0.301029995663981,0.909780212641189,0.4060143),
c("GO:0071236","cellular response to antibiotic",0.519384561891516,-6.41330064608395,-1.10213492512537,1.77815125038364,0.915173797687403,0.40636396),
c("GO:0035329","hippo signaling",0.0782336578581363,-5.94351949618411,-2.26832609933644,1,0.871257654628638,0.40775527),
c("GO:0008643","carbohydrate transport",0.356397774687065,-5.65457555761182,3.74125383474889,1.6232492903979,0.946550669427103,0.40872846),
c("GO:0000280","nuclear division",2.11230876216968,5.73720219622267,4.64565281011882,2.38738982633873,0.912590806852045,0.40975478),
c("GO:0046825","regulation of protein export from nucleus",0.0260778859527121,-0.219080396669797,-1.73792041647028,0.602059991327962,0.915081497835556,0.4103306),
c("GO:0044085","cellular component biogenesis",11.4481919332406,5.91196824905834,4.31749838780789,3.11991541025799,0.91595096568776,0.41155765),
c("GO:0018198","peptidyl-cysteine modification",0.226008344923505,0.036592376418185,6.90638667918531,1.43136376415899,0.913468113705011,0.41172096),
c("GO:0009790","embryo development",4.45931849791377,5.96068852349577,-1.78101692922439,2.71096311899528,0.876880851925066,0.4121783),
c("GO:0048580","regulation of post-embryonic development",0.0434631432545202,-1.84401155935905,-1.3252994491706,0.778151250383644,0.912888001039322,0.41345502),
c("GO:0009453","energy taxis",0.182545201668985,-6.74025416768023,0.15731186827793,1.34242268082221,0.946377344102495,0.41407866),
c("GO:0090287","regulation of cellular response to growth factor stimulus",0.530250347705146,-4.12957754500302,-5.60125617571817,1.79239168949825,0.898921180828885,0.41464944),
c("GO:0048469","cell maturation",1.44297635605007,6.63072910011859,-0.300619067205229,2.22271647114758,0.869248125220905,0.41571186),
c("GO:0048285","organelle fission",2.22531293463143,5.6341661532398,4.67241947243832,2.40993312333129,0.917344958251192,0.41571478),
c("GO:0051418","microtubule nucleation by microtubule organizing center",0.0260778859527121,5.0466935131715,5.12206027509184,0.602059991327962,0.921789695312779,0.41616159),
c("GO:0001505","regulation of neurotransmitter levels",1.06050069541029,2.57315951525206,-5.87698621481652,2.0899051114394,0.906043081108278,0.41719741),
c("GO:0002066","columnar/cuboidal epithelial cell development",0.00869262865090403,7.16420265455829,0.536024183673277,0.301029995663981,0.903479872821164,0.41786422),
c("GO:0046627","negative regulation of insulin receptor signaling pathway",0.226008344923505,-3.99149025561102,-5.80213990916196,1.43136376415899,0.880912321234107,0.4189154),
c("GO:0098754","detoxification",0.712795549374131,-6.59666744604965,-0.715791597679824,1.91907809237607,0.943019417706022,0.41955605),
c("GO:0030865","cortical cytoskeleton organization",0.547635605006954,5.53360333000619,4.99326425339728,1.80617997398389,0.919780960700535,0.42069923),
c("GO:0051101","regulation of DNA binding",0.139082058414465,1.07857392761227,-1.93994029987194,1.23044892137827,0.930046992594561,0.421507),
c("GO:0022416","chaeta development",0.712795549374131,6.44004369743041,-2.17075404411437,1.91907809237607,0.873408972626351,0.42324283),
c("GO:0060541","respiratory system development",2.1470792767733,6.08677422985382,-1.95272137432862,2.39445168082622,0.87266807565095,0.42340791),
c("GO:0007618","mating",1.22566063977747,5.13542989936431,2.0183605280478,2.15228834438306,0.963471275604678,0.42437997),
c("GO:0009791","post-embryonic development",5.37204450625869,6.04989718687215,-1.71912970624249,2.79169064902012,0.873989394478935,0.42543277),
c("GO:0072521","purine-containing compound metabolic process",1.79068150208623,-1.24758937707103,6.47722344490908,2.31597034545692,0.881458407985718,0.42558916),
c("GO:1903429","regulation of cell maturation",0.147774687065369,-3.31063395543581,-2.97772631853498,1.25527250510331,0.898652239757277,0.4257417),
c("GO:0015748","organophosphate ester transport",0.365090403337969,-5.70795202299855,3.7233188373997,1.63346845557959,0.946433294610125,0.42615256),
c("GO:0060401","cytosolic calcium ion transport",0.147774687065369,-5.80259244528365,2.98204588943043,1.25527250510331,0.948641301301162,0.4283934),
c("GO:0072488","ammonium transmembrane transport",0.0173852573018081,-5.73317210309303,2.71033216047853,0.477121254719662,0.937335925957865,0.4283934),
c("GO:0007034","vacuolar transport",0.530250347705146,-5.84756847799537,3.17908899442568,1.79239168949825,0.920656371493109,0.43130583),
c("GO:0014016","neuroblast differentiation",0.425938803894298,6.24890814946106,-1.21014215502705,1.69897000433602,0.858442031683122,0.43137807),
c("GO:1903311","regulation of mRNA metabolic process",1.34735744089013,-1.40304741750216,-6.29616703277284,2.19312459835446,0.878998070936841,0.43244786),
c("GO:0006979","response to oxidative stress",1.17350486787204,-6.84921501248207,-1.35477398423994,2.13353890837022,0.949513576223123,0.43324672),
c("GO:0046677","response to antibiotic",0.987482614742698,-6.68447934577719,-0.79055762901193,2.05690485133647,0.942696651727502,0.43406655),
c("GO:0006777","Mo-molybdopterin cofactor biosynthetic process",0.0521557719054242,-1.33457433638266,6.63115115806799,0.845098040014257,0.873881806558823,0.43521863),
c("GO:0000902","cell morphogenesis",4.35500695410292,6.84243015941567,-0.771957779465313,2.70070371714502,0.876683635488592,0.43613287),
c("GO:0007259","receptor signaling pathway via JAK-STAT",0.0695410292072323,-6.06841642395187,-2.33158681659632,0.954242509439325,0.872607900375383,0.43784675),
c("GO:0034976","response to endoplasmic reticulum stress",0.704102920723227,-6.61300546185668,-1.59593265529989,1.91381385238372,0.922360117918075,0.43803902),
c("GO:0042058","regulation of epidermal growth factor receptor signaling pathway",0.382475660639778,-3.93738415128614,-5.90589715284822,1.65321251377534,0.895978132165786,0.43816166),
c("GO:0032968","positive regulation of transcription elongation from RNA polymerase II promoter",0.147774687065369,-0.400677274768004,-6.72657713334513,1.25527250510331,0.879808731157282,0.43828877),
c("GO:0016485","protein processing",0.799721835883171,-0.221179164762734,6.89223010649585,1.96848294855394,0.92102482048531,0.43836599),
c("GO:0008078","mesodermal cell migration",0.173852573018081,-6.34364823615899,2.87671289774561,1.32221929473392,0.929977841897879,0.43943142),
c("GO:0006891","intra-Golgi vesicle-mediated transport",0.234700973574409,-4.9460319452354,3.10031311325748,1.44715803134222,0.929606908762798,0.43966452),
c("GO:0009303","rRNA transcription",0.0608484005563282,-2.17651192307878,6.59043953258652,0.903089986991944,0.882567937268647,0.43992002),
c("GO:0043170","macromolecule metabolic process",29.4506258692629,-1.19379929136328,5.22122177227483,3.53007156883738,0.924530126701077,0.44058306),
c("GO:1901879","regulation of protein depolymerization",0.252086230876217,-1.31527244114413,-4.77267410272422,1.47712125471966,0.893590334956743,0.44180473),
c("GO:0097696","receptor signaling pathway via STAT",0.0695410292072323,-5.9464173437011,-2.17924099987585,0.954242509439325,0.872607900375383,0.44186726),
c("GO:0010628","positive regulation of gene expression",1.69506258692629,-0.680837109573045,-6.05702909536705,2.29225607135648,0.86151538158765,0.44220273),
c("GO:1901564","organonitrogen compound metabolic process",24.9217663421419,-0.593410331842957,5.71946680328295,3.45757914699576,0.9153908115182,0.44225545),
c("GO:0009636","response to toxic substance",0.99095966620306,-6.77054176946691,-0.789261265602642,2.06069784035361,0.942676829842967,0.4431364),
c("GO:0050803","regulation of synapse structure or activity",1.64290681502086,2.17615059787469,-5.59140205306814,2.27875360095283,0.901660130623404,0.44328772),
c("GO:0006101","citrate metabolic process",0.0347705146036161,2.38308174519673,7.44091887350065,0.698970004336019,0.917431851961957,0.4439689),
c("GO:0048581","negative regulation of post-embryonic development",0.0173852573018081,-1.65885361986236,-1.83284339629697,0.477121254719662,0.901643646973983,0.44401625),
c("GO:0007498","mesoderm development",0.851877607788595,7.2127440271278,-0.74534595413118,1.99563519459755,0.899597469803937,0.44562168),
c("GO:0044260","cellular macromolecule metabolic process",20.5146036161335,-0.761785063572614,5.70185349630354,3.37309598707873,0.888600499841923,0.44593109),
c("GO:0048880","sensory system development",3.07719054242003,6.15473618205245,-1.89182245264587,2.55022835305509,0.867335192362364,0.446366),
c("GO:0090501","RNA phosphodiester bond hydrolysis",0.912726008344924,-1.77070257200279,6.57954014100703,2.02530586526477,0.88452735341781,0.44640072),
c("GO:0035295","tube development",5.96314325452017,5.99912341298152,-1.85553862995866,2.83695673705955,0.872306438023776,0.4469581),
c("GO:0010453","regulation of cell fate commitment",0.269471488178025,-2.26045740886575,-3.13953563803079,1.50514997831991,0.899758731898139,0.4470406),
c("GO:0007548","sex differentiation",0.956189151599444,6.21405104184383,-0.134323770174258,2.04532297878666,0.892762221291155,0.44711786),
c("GO:0007366","periodic partitioning by pair rule gene",0.104311543810848,6.55406009992603,-2.79427601590548,1.11394335230684,0.901395300530546,0.44726537),
c("GO:1901184","regulation of ERBB signaling pathway",0.382475660639778,-4.17692738877446,-5.66006962512441,1.65321251377534,0.897922675684924,0.45069559),
c("GO:0010629","negative regulation of gene expression",2.87726008344923,-1.26219999297927,-5.89449197301751,2.52113808370404,0.852308950004991,0.45081948),
c("GO:0051246","regulation of protein metabolic process",6.08484005563282,-1.10116401753948,-5.84146401016644,2.84571801796666,0.866159380920744,0.45100454),
c("GO:1990542","mitochondrial transmembrane transport",0.669332406119611,-5.17605725493978,3.05356257883958,1.89209460269048,0.927747554267299,0.45138638),
c("GO:0046626","regulation of insulin receptor signaling pathway",0.391168289290681,-4.09818112718573,-5.74635241222497,1.66275783168157,0.897712864762558,0.45160723),
c("GO:0071772","response to BMP",0.139082058414465,-6.88714131837791,-0.392055712724252,1.23044892137827,0.942946328047798,0.45289227),
c("GO:0043244","regulation of protein-containing complex disassembly",0.339012517385257,-2.59995368116326,-6.51378591358178,1.60205999132796,0.892681550003176,0.45302077),
c("GO:0051604","protein maturation",1.086578581363,-0.9318129736859,5.73712470304048,2.10037054511756,0.921380248147488,0.45320974),
c("GO:0048138","germ-line cyst encapsulation",0.165159944367177,6.29529828455749,-0.55483240387332,1.30102999566398,0.873727888542864,0.45371081),
c("GO:0007229","integrin-mediated signaling pathway",0.104311543810848,-5.93008924346834,-2.44150957965583,1.11394335230684,0.868467349902069,0.45454091),
c("GO:0044770","cell cycle phase transition",0.417246175243394,2.86167360523233,1.33225233651949,1.69019608002851,0.948977419313178,0.45477267),
c("GO:0048015","phosphatidylinositol-mediated signaling",0.0956189151599444,-5.81620923096246,-2.22378702568525,1.07918124604762,0.869201819269321,0.45703436),
c("GO:0035146","tube fusion",0.182545201668985,7.02117214507862,-1.68348575850835,1.34242268082221,0.879740317143601,0.45740587),
c("GO:0034641","cellular nitrogen compound metabolic process",16.307371349096,-0.864667592318908,5.5599306177461,3.27346427262135,0.897346832501032,0.45744115),
c("GO:0010821","regulation of mitochondrion organization",0.286856745479833,-1.29598166803102,-6.02214274959095,1.53147891704226,0.890153237102844,0.45809281),
c("GO:0051952","regulation of amine transport",0.104311543810848,-0.310339028798901,-2.00210324664304,1.11394335230684,0.913887160973957,0.45896427),
c("GO:0048732","gland development",1.52121001390821,6.27962555716951,-2.02961498650428,2.24551266781415,0.868599004440409,0.45900461),
c("GO:0008592","regulation of Toll signaling pathway",0.460709318497914,-3.91418358160347,-5.82122156756547,1.73239375982297,0.896158350051342,0.4593009),
c("GO:0045880","positive regulation of smoothened signaling pathway",0.399860917941586,-3.60929285596161,-5.89635787803088,1.67209785793572,0.876471789106141,0.46022687),
c("GO:0061844","antimicrobial humoral immune response mediated by antimicrobial peptide",0.00869262865090403,-5.77332814943469,0.0941311750614121,0.301029995663981,0.951632632338217,0.46032012),
c("GO:0032507","maintenance of protein location in cell",0.182545201668985,-6.11879160632947,2.91187051618123,1.34242268082221,0.92859761699157,0.46091243),
c("GO:0051276","chromosome organization",4.50278164116829,5.68762865199472,4.54418939024412,2.71516735784846,0.910397865895608,0.46127976),
c("GO:0009799","specification of symmetry",0.156467315716273,7.0015728923517,-2.35775746526082,1.27875360095283,0.905082347299025,0.46130162),
c("GO:0006950","response to stress",10.1182197496523,-6.6244799986011,-1.29687520173468,3.06632592536204,0.944852206390375,0.46228996),
c("GO:0006869","lipid transport",0.860570236439499,-5.81451573570678,3.45056780274376,2,0.936422400259498,0.46238615),
c("GO:0006914","autophagy",1.086578581363,0.937630213786746,6.11897678317242,2.10037054511756,0.911262336699908,0.4632494),
c("GO:0009112","nucleobase metabolic process",0.191237830319889,-1.04351615457867,7.00509445742039,1.36172783601759,0.873862716045002,0.46350643),
c("GO:0006544","glycine metabolic process",0.0695410292072323,0.698589826515334,7.39015880738268,0.954242509439325,0.90505306141665,0.4657377),
c("GO:0048017","inositol lipid-mediated signaling",0.104311543810848,-5.80228456423628,-2.27462016791492,1.11394335230684,0.868289602939861,0.46654946),
c("GO:0090092","regulation of transmembrane receptor protein serine/threonine kinase signaling pathway",0.469401947148818,-4.04216177327064,-5.65902899617679,1.74036268949424,0.89597770798021,0.46709678),
c("GO:0050794","regulation of cellular process",34.5184283727399,-1.71263888748066,-5.07602799530836,3.59900923982334,0.870881330127534,0.46879876),
c("GO:0030723","ovarian fusome organization",0.0956189151599444,6.15926447905574,1.23254279117243,1.07918124604762,0.831755939363843,0.46935043),
c("GO:0007041","lysosomal transport",0.243393602225313,-5.98817856124609,3.23662805349618,1.46239799789896,0.925283006027746,0.47075226),
c("GO:0007224","smoothened signaling pathway",0.121696801112656,-5.85168077405412,-2.44471524751654,1.17609125905568,0.866820789936284,0.47327623),
c("GO:0051640","organelle localization",1.9297635605007,-5.73203236128057,3.02833374707765,2.34830486304816,0.917578962723629,0.47638576),
c("GO:0007417","central nervous system development",2.41655076495132,6.19267782564287,-1.82872431639889,2.4456042032736,0.862727009261897,0.47849022),
c("GO:0050804","modulation of chemical synaptic transmission",1.25173852573018,-3.75297314169751,-5.47501282316501,2.16136800223497,0.894742910806611,0.47862383),
c("GO:0002831","regulation of response to biotic stimulus",1.60813630041725,-3.43283591100018,-5.91340419867596,2.26951294421792,0.892849357331085,0.47922354),
c("GO:0032508","DNA duplex unwinding",0.417246175243394,5.65610057135298,4.94219986227815,1.69019608002851,0.922815889826529,0.47969494),
c("GO:0090066","regulation of anatomical structure size",2.07753824756606,1.96686826516926,-5.47307271219408,2.38021124171161,0.899133525609151,0.4806292),
c("GO:0030162","regulation of proteolysis",2.06015299026426,-0.919866122441171,-6.32269026483924,2.37657695705651,0.870832877980825,0.48105604),
c("GO:0008063","Toll signaling pathway",0.13038942976356,-5.85617087929,-2.50047387315912,1.20411998265592,0.86607024245933,0.48118474),
c("GO:0032984","protein-containing complex disassembly",0.460709318497914,5.11795945598483,4.83385950412072,1.73239375982297,0.928377185792927,0.48156987),
c("GO:0016311","dephosphorylation",1.75591098748261,0.227459048205123,5.81123629142171,2.30749603791321,0.89695421231758,0.4827675),
c("GO:0006491","N-glycan processing",0.156467315716273,0.216747735591135,7.05029615029349,1.27875360095283,0.908773636048264,0.48331169),
c("GO:0019935","cyclic-nucleotide-mediated signaling",0.156467315716273,-5.70226985406,-2.39660668365868,1.27875360095283,0.863280154987941,0.48379178),
c("GO:0042221","response to chemical",10.239916550765,-6.62489204045164,-1.23571402371644,3.07151380509509,0.944765729824717,0.48405148),
c("GO:0048565","digestive tract development",0.964881780250348,6.36342016000166,-2.07811910506887,2.04921802267018,0.87044558573425,0.48442025),
c("GO:0010876","lipid localization",0.99095966620306,-4.93293511524101,2.78380317599542,2.06069784035361,0.947244660134391,0.48538566),
c("GO:0044238","primary metabolic process",36.500347705146,-1.77849308823684,5.11400122860303,3.6232492903979,0.928784204209555,0.48546604),
c("GO:0044782","cilium organization",1.37343532684284,5.67745376137001,4.35448015266496,2.20139712432045,0.910920356451806,0.4856665),
c("GO:0048608","reproductive structure development",0.704102920723227,5.82998805923293,-1.24768626448713,1.91381385238372,0.861397169878072,0.48617452),
c("GO:0003341","cilium movement",0.573713490959666,3.32128413494297,4.01905740344022,1.82607480270083,0.949643815517279,0.48768078),
c("GO:0007186","G protein-coupled receptor signaling pathway",1.92107093184979,-4.86085904965935,-2.93998208788919,2.34635297445064,0.832378874517894,0.48933249),
c("GO:0043087","regulation of GTPase activity",0.808414464534075,2.52551884062858,-7.07271675266854,1.9731278535997,0.914634838880743,0.48996863),
c("GO:0031123","RNA 3'-end processing",0.678025034770515,-1.79924718061836,6.65995568663407,1.89762709129044,0.884870215907096,0.49026733),
c("GO:0051259","protein complex oligomerization",0.173852573018081,4.99530471747755,5.03197239571896,1.32221929473392,0.928106425283543,0.49072712),
c("GO:0000082","G1/S transition of mitotic cell cycle",0.104311543810848,2.28595021156512,-1.36668897059917,1.11394335230684,0.951530492923864,0.49089804),
c("GO:0036335","intestinal stem cell homeostasis",0.252086230876217,3.31089535169159,-6.06147974913699,1.47712125471966,0.910967980114427,0.4914163),
c("GO:0009743","response to carbohydrate",0.330319888734353,-6.86496790957855,-0.537166683828755,1.5910646070265,0.939991718894912,0.4924171),
c("GO:0042749","regulation of circadian sleep/wake cycle",0.399860917941586,0.573828353674898,-4.95671476160301,1.67209785793572,0.910555815553303,0.49296425),
c("GO:0007469","antennal development",0.226008344923505,6.85074566876916,-1.41975887728776,1.43136376415899,0.868043667829159,0.4940594),
c("GO:0007279","pole cell formation",0.182545201668985,6.1228412978965,-0.642362587342945,1.34242268082221,0.853526364533779,0.49491394),
c("GO:0014059","regulation of dopamine secretion",0.0782336578581363,2.00543025338678,-6.47864602249572,1,0.908757292205541,0.49493204),
c("GO:0009653","anatomical structure morphogenesis",13.0302503477051,6.77336782865171,-0.871476972999286,3.17609125905568,0.88360343662326,0.49506652),
c("GO:0045454","cell redox homeostasis",0.182545201668985,1.78618005267366,-5.30465345076762,1.34242268082221,0.879755538429628,0.49541844),
c("GO:0018193","peptidyl-amino acid modification",3.68567454798331,-0.618650670302541,5.95179624111642,2.62838893005031,0.888914254338432,0.49594231),
c("GO:0006259","DNA metabolic process",2.65994436717663,-1.32262316051319,6.35331929034059,2.48713837547719,0.868162316756782,0.49781304),
c("GO:1901700","response to oxygen-containing compound",2.74687065368567,-6.60048137778705,-0.876488466376481,2.50105926221775,0.936278605137863,0.4983632),
c("GO:0007254","JNK cascade",0.147774687065369,-5.69347083858019,-2.15638893067093,1.25527250510331,0.857884903880808,0.50089111),
c("GO:0044237","cellular metabolic process",35.5876216968011,-1.80194558193318,5.09769169273823,3.61225390609644,0.905463572578679,0.50107259),
c("GO:0042063","gliogenesis",0.721488178025035,6.12782083324106,-1.32643281434929,1.92427928606188,0.851889727416885,0.50124181),
c("GO:0046434","organophosphate catabolic process",0.45201668984701,-3.06355699802502,5.79539678571094,1.72427586960079,0.884254186554312,0.50125738),
c("GO:0050789","regulation of biological process",37.1436022253129,-1.580480491512,-5.04730967713875,3.63083451782805,0.888693108573177,0.50195478),
c("GO:0031146","SCF-dependent proteasomal ubiquitin-dependent protein catabolic process",0.53894297635605,-1.34776883113845,5.65799874111836,1.79934054945358,0.894389258781555,0.50255374),
c("GO:0044283","small molecule biosynthetic process",1.97322670375522,-1.40848789102153,4.75337525250994,2.35793484700045,0.888471975789601,0.50519309),
c("GO:0060828","regulation of canonical Wnt signaling pathway",0.791029207232267,-3.74061158564272,-5.63738375987078,1.96378782734556,0.889437716070446,0.50571449),
c("GO:0007215","glutamate receptor signaling pathway",0.234700973574409,-5.60100464972218,-2.51447674901197,1.44715803134222,0.859310498265014,0.50607502),
c("GO:1905039","carboxylic acid transmembrane transport",0.895340751043115,-5.35092559556971,3.1936174819742,2.01703333929878,0.917860097887516,0.50618148),
c("GO:0017004","cytochrome complex assembly",0.252086230876217,6.10809997827983,4.6482514634125,1.47712125471966,0.925593592340782,0.50677318),
c("GO:0030203","glycosaminoglycan metabolic process",0.286856745479833,0.276278834859434,7.18507725887856,1.53147891704226,0.924233167073938,0.5083335),
c("GO:0042254","ribosome biogenesis",1.9384561891516,6.00521699368993,4.55719068144385,2.35024801833416,0.917881305968455,0.50878367),
c("GO:0009991","response to extracellular stimulus",1.49513212795549,-6.84754668509767,-0.931706055972148,2.2380461031288,0.946463934319711,0.51139348),
c("GO:1990778","protein localization to cell periphery",0.565020862308762,-5.2291508766182,2.7130708160998,1.81954393554187,0.920922016831371,0.51245564),
c("GO:0098876","vesicle-mediated transport to the plasma membrane",0.417246175243394,-5.39950941072452,2.95269175397678,1.69019608002851,0.917534920971497,0.51305556),
c("GO:0006949","syncytium formation",0.278164116828929,7.12881404705619,-0.23384857359149,1.51851393987789,0.885579070796647,0.51311889),
c("GO:0010769","regulation of cell morphogenesis involved in differentiation",0.139082058414465,1.17817069434592,-5.75492018431245,1.23044892137827,0.906724199352717,0.51312754),
c("GO:0061983","meiosis II cell cycle process",0.217315716272601,3.77137066950318,1.3192587783121,1.41497334797082,0.926367966541436,0.51332183),
c("GO:0002164","larval development",1.42559109874826,6.63861311309998,-2.00026542224422,2.21748394421391,0.880764431757203,0.5139174),
c("GO:0006040","amino sugar metabolic process",0.330319888734353,2.64284273877884,7.00416492458708,1.5910646070265,0.938996051796574,0.51453357),
c("GO:0015849","organic acid transport",1.01703755215577,-5.65493184291274,3.58679333248186,2.07188200730613,0.940908805874986,0.51527001),
c("GO:1902903","regulation of supramolecular fiber organization",1.04311543810848,-2.70116925152302,-5.34165007662157,2.08278537031645,0.880667034193799,0.51579032),
c("GO:0006403","RNA localization",1.5038247566064,-4.99113454657281,2.78408860431546,2.2405492482826,0.944898363162867,0.51613313),
c("GO:0051231","spindle elongation",0.113004172461752,5.27914681189915,3.85362817529944,1.14612803567824,0.908362401263777,0.51739877),
c("GO:0044403","biological process involved in symbiotic interaction",0.234700973574409,-2.66635284143588,0.937057552563362,1.44715803134222,0.991003565959069,0.51759619),
c("GO:0048872","homeostasis of number of cells",0.312934631432545,3.18193096593318,-5.9417276740668,1.56820172406699,0.909240213644295,0.51814413),
c("GO:0090087","regulation of peptide transport",0.147774687065369,-0.496122953603954,-2.11370047632449,1.25527250510331,0.911390715335457,0.51845265),
c("GO:0006260","DNA replication",0.94749652294854,-2.23329935527661,5.56902417012453,2.04139268515822,0.888806353632164,0.51884071),
c("GO:0032880","regulation of protein localization",0.94749652294854,-0.424925690559766,-4.159735085836,2.04139268515822,0.898064845384203,0.51988169),
c("GO:0006839","mitochondrial transport",0.712795549374131,-5.86619935639775,3.1908468207032,1.91907809237607,0.918377152269538,0.52042475),
c("GO:0048522","positive regulation of cellular process",14.3341446453408,-1.59862322502909,-5.05502452127569,3.21748394421391,0.849181422357183,0.52066583),
c("GO:0008038","neuron recognition",0.999652294853964,6.19737131107365,-1.27771473704304,2.06445798922692,0.839849275496657,0.52086764),
c("GO:0009889","regulation of biosynthetic process",12.6390820584145,-1.25541082972389,-5.62236096979461,3.16286299332193,0.858126119117748,0.52103363),
c("GO:0072523","purine-containing compound catabolic process",0.226008344923505,-1.59290827588358,6.73456021086854,1.43136376415899,0.880114602604341,0.52109305),
c("GO:0030111","regulation of Wnt signaling pathway",0.869262865090403,-3.59887768766409,-5.72597089278893,2.00432137378264,0.889642529508808,0.52346853),
c("GO:0007010","cytoskeleton organization",5.06780250347705,5.66051395295414,4.59288410767146,2.7664128471124,0.909114358486957,0.52369207),
c("GO:0071704","organic substance metabolic process",38.8734353268428,-1.53127160636204,5.06242477317396,3.65059889817266,0.927943614386334,0.52373412),
c("GO:2000648","positive regulation of stem cell proliferation",0.0347705146036161,-1.55033223226382,-0.83831359992208,0.698970004336019,0.912269616892974,0.52473087),
c("GO:0006952","defense response",3.32927677329624,-6.73006771113793,-1.27336592676621,2.58433122436753,0.943566873769306,0.52475751),
c("GO:0000165","MAPK cascade",0.304242002781641,-5.48625353624698,-2.52689804329411,1.55630250076729,0.855911553614368,0.52604907),
c("GO:0035215","genital disc development",0.434631432545202,6.6297276158149,-1.86648112856984,1.70757017609794,0.868899051117759,0.52611292),
c("GO:0043171","peptide catabolic process",0.252086230876217,-2.12592113714858,6.45384591998416,1.47712125471966,0.892119479110802,0.52617074),
c("GO:0007483","genital disc morphogenesis",0.191237830319889,6.87865544721591,-1.49340092343468,1.36172783601759,0.862290242761734,0.52652472),
c("GO:0055090","acylglycerol homeostasis",0.304242002781641,3.0847401191267,-5.78246952391439,1.55630250076729,0.907455419622396,0.52657155),
c("GO:1901362","organic cyclic compound biosynthetic process",4.24200278164117,-1.68104341958731,6.09378385253241,2.68930885912362,0.884192666910664,0.52722777),
c("GO:1905954","positive regulation of lipid localization",0.173852573018081,-0.0649327766106756,-2.99366064482335,1.32221929473392,0.894577437650641,0.52755301),
c("GO:1901657","glycosyl compound metabolic process",0.382475660639778,1.76510669393539,5.35742579661495,1.65321251377534,0.938174851483946,0.52765712),
c("GO:0006820","anion transport",1.86891515994437,-5.71072758697453,3.45472830343173,2.33445375115093,0.936862125498372,0.52819677),
c("GO:0006298","mismatch repair",0.113004172461752,-3.15092373496314,3.79170301336321,1.14612803567824,0.857233505084295,0.53077683),
c("GO:0106030","neuron projection fasciculation",0.191237830319889,6.2874749921564,0.941264552285217,1.36172783601759,0.83295174272623,0.53110918),
c("GO:0015931","nucleobase-containing compound transport",1.19958275382476,-5.67667032160281,3.51717831311226,2.14301480025409,0.938171389221673,0.53199638),
c("GO:0051716","cellular response to stimulus",15.2990264255911,-6.58784653766644,-1.21481840035797,3.24575935596728,0.912965280783602,0.5322034),
c("GO:0099177","regulation of trans-synaptic signaling",1.25173852573018,-3.72205884518882,-5.48318872668992,2.16136800223497,0.896163745109097,0.53220603),
c("GO:0000413","protein peptidyl-prolyl isomerization",0.286856745479833,-0.0241755437803993,6.87582585452832,1.53147891704226,0.911622041137199,0.53222571),
c("GO:0044057","regulation of system process",0.573713490959666,-0.236433099700111,-3.88323962789825,1.82607480270083,0.908922342512486,0.53253253),
c("GO:0003382","epithelial cell morphogenesis",0.269471488178025,6.83545341760714,-0.351400065105554,1.50514997831991,0.863743099386493,0.53380456),
c("GO:0048869","cellular developmental process",14.8035465924896,6.77562218937731,-0.818007014048834,3.23146959043068,0.860949053552338,0.53407607),
c("GO:0001700","embryonic development via the syncytial blastoderm",1.44297635605007,6.23355326100778,-2.35128068299728,2.22271647114758,0.883263039843153,0.53520896),
c("GO:0010257","NADH dehydrogenase complex assembly",0.304242002781641,6.05961520914393,4.68619057114355,1.55630250076729,0.92435266106816,0.53552275),
c("GO:0006805","xenobiotic metabolic process",0.139082058414465,-5.95380822681403,-0.0508222628754304,1.23044892137827,0.888546126291729,0.53579578),
c("GO:0051607","defense response to virus",0.330319888734353,-6.30763638456018,-0.317548344487393,1.5910646070265,0.944477596691502,0.5360133),
c("GO:0090303","positive regulation of wound healing",0.121696801112656,0.186362298640756,-4.69857144722507,1.17609125905568,0.89498487098361,0.53668347),
c("GO:0031098","stress-activated protein kinase signaling cascade",0.199930458970793,-5.61740344679753,-2.25857297534534,1.38021124171161,0.854706536542565,0.53678561),
c("GO:0007628","adult walking behavior",0.121696801112656,5.15004674791534,-4.6873139180325,1.17609125905568,0.939840183356305,0.53740402),
c("GO:0006639","acylglycerol metabolic process",0.295549374130737,2.22318801773019,6.97844782942031,1.54406804435028,0.923711158672487,0.53752898),
c("GO:0007601","visual perception",0.573713490959666,5.66555207269413,-4.35727922156512,1.82607480270083,0.933770008801084,0.53876188),
c("GO:0030713","ovarian follicle cell stalk formation",0.104311543810848,6.2951704607919,-0.387697900846278,1.11394335230684,0.852028183487884,0.54076135),
c("GO:0048232","male gamete generation",2.75556328233658,5.37419441015063,-3.31400741366175,2.50242711998443,0.903495354642879,0.54137186),
c("GO:0070848","response to growth factor",0.425938803894298,-6.77796727412345,-0.557609315509458,1.69897000433602,0.939757950620427,0.54175059),
c("GO:0042592","homeostatic process",4.17246175243394,1.36702215175814,-5.33455844286952,2.68214507637383,0.890777895512227,0.5441645),
c("GO:0009612","response to mechanical stimulus",0.347705146036161,-6.82939059333416,-0.066964469670249,1.61278385671974,0.947650248882169,0.54530992),
c("GO:0006022","aminoglycan metabolic process",0.478094575799722,0.120782980695755,7.12280026433536,1.7481880270062,0.922152441469271,0.54554078),
c("GO:0033962","P-body assembly",0.0782336578581363,5.20864696987551,5.32915260279895,1,0.928455822168323,0.54565088),
c("GO:0035556","intracellular signal transduction",3.53789986091794,-4.66631762581086,-3.05327245279158,2.61066016308988,0.820714529678423,0.54571942),
c("GO:0015985","energy coupled proton transport, down electrochemical gradient",0.208623087621697,-5.84502088194983,3.67522284606648,1.39794000867204,0.928797957047565,0.54613806),
c("GO:0006470","protein dephosphorylation",0.938803894297636,-0.512052258667372,6.31225413074904,2.03742649794062,0.87969871353917,0.54682449),
c("GO:0035214","eye-antennal disc development",0.53894297635605,6.60186640497061,-1.80233905570249,1.79934054945358,0.866222471165172,0.54801644),
c("GO:0051258","protein polymerization",0.330319888734353,5.19188398795659,4.7921998408534,1.5910646070265,0.923796733082983,0.5481007),
c("GO:0046620","regulation of organ growth",0.556328233657858,-2.74759634339833,-3.20152751752053,1.81291335664286,0.890060418282057,0.54952039),
c("GO:0045995","regulation of embryonic development",0.417246175243394,-2.66460958054786,-2.91245601561061,1.69019608002851,0.894991659638214,0.5507545),
c("GO:0070925","organelle assembly",3.49443671766342,5.6471130090455,4.57175991865023,2.60530504614111,0.902943268613512,0.55189134),
c("GO:0035186","syncytial blastoderm mitotic cell cycle",0.147774687065369,5.21869539803253,-1.29261185386919,1.25527250510331,0.86701615440271,0.55254087),
c("GO:0045292","mRNA cis splicing, via spliceosome",0.139082058414465,-2.52517736901534,6.74262658781882,1.23044892137827,0.899109323027541,0.55322599),
c("GO:0051588","regulation of neurotransmitter transport",0.243393602225313,-0.259996556713493,-2.77726577420328,1.46239799789896,0.907547543882348,0.55349588),
c("GO:0007423","sensory organ development",3.86821974965229,6.32623708657069,-1.8235490423197,2.64933485871214,0.854045898336885,0.5536515),
c("GO:0007475","apposition of dorsal and ventral imaginal disc-derived wing surfaces",0.147774687065369,6.92648717755965,-1.53136192367276,1.25527250510331,0.864479249414858,0.55395629),
c("GO:0042332","gravitaxis",0.217315716272601,-6.75546292390335,0.0522114850462991,1.41497334797082,0.940156876099338,0.55416867),
c("GO:0034404","nucleobase-containing small molecule biosynthetic process",0.113004172461752,-1.7600243718711,6.84698876039567,1.14612803567824,0.867741192889954,0.55464318),
c("GO:0042387","plasmatocyte differentiation",0.113004172461752,5.98529788745629,0.0551885323961359,1.14612803567824,0.891224458782441,0.55536615),
c("GO:0031338","regulation of vesicle fusion",0.0695410292072323,0.149851687997783,-4.496263336865,0.954242509439325,0.883004723591943,0.55552549),
c("GO:0007219","Notch signaling pathway",0.40855354659249,-5.40375473708954,-2.62006911102404,1.68124123737559,0.85226902168254,0.5560959),
c("GO:0006638","neutral lipid metabolic process",0.295549374130737,2.21507265721976,7.01190204798923,1.54406804435028,0.925030035497423,0.55761762),
c("GO:0044270","cellular nitrogen compound catabolic process",1.43428372739917,-2.0215117258144,6.22945651325031,2.22010808804005,0.883928101064574,0.55866476),
c("GO:0006378","mRNA polyadenylation",0.182545201668985,-2.04586480448378,6.95775190148815,1.34242268082221,0.895941417199126,0.55866891),
c("GO:0006913","nucleocytoplasmic transport",1.0691933240612,-5.75131551198964,3.19099650649559,2.09342168516224,0.912277842379012,0.55891658),
c("GO:0016579","protein deubiquitination",0.417246175243394,-0.0481766622759785,6.58978459663967,1.69019608002851,0.909515903647193,0.5592206),
c("GO:0033993","response to lipid",0.469401947148818,-6.81449701827979,-0.586252300116871,1.74036268949424,0.939227262224102,0.55934471),
c("GO:0031109","microtubule polymerization or depolymerization",0.278164116828929,5.23973726638744,5.08242876705733,1.51851393987789,0.92097613679424,0.55959382),
c("GO:0050919","negative chemotaxis",0.208623087621697,-6.63377693367759,-0.210566477289702,1.39794000867204,0.934221288471533,0.56018291),
c("GO:0006720","isoprenoid metabolic process",0.312934631432545,2.16785225806972,6.99915601676781,1.56820172406699,0.924639401592839,0.56036738),
c("GO:0046112","nucleobase biosynthetic process",0.13038942976356,-1.20759523894317,6.77200902470029,1.20411998265592,0.864275414164974,0.56079502),
c("GO:0018212","peptidyl-tyrosine modification",0.425938803894298,-0.0743837584205908,6.50065210567845,1.69897000433602,0.9083774212774,0.56204069),
c("GO:0009798","axis specification",1.66029207232267,6.45689575186047,-2.35469083924092,2.28330122870355,0.881033983885422,0.56449566),
c("GO:0032101","regulation of response to external stimulus",2.21662030598053,-3.27379050039444,-5.85433869739503,2.40823996531185,0.889071177571168,0.5655634),
c("GO:0016241","regulation of macroautophagy",0.295549374130737,-1.01564038730247,-6.92706039112729,1.54406804435028,0.890914214750568,0.5655879),
c("GO:0009225","nucleotide-sugar metabolic process",0.147774687065369,-0.91460597099971,7.1010745892231,1.25527250510331,0.872004943785231,0.56628871),
c("GO:0007286","spermatid development",1.06050069541029,5.94467449253177,-0.702935522752208,2.0899051114394,0.844952125040534,0.5693714),
c("GO:0006810","transport",16.6116133518776,-5.5430409870581,3.30147410879485,3.28148788794008,0.928686748709816,0.5701158),
c("GO:0198738","cell-cell signaling by wnt",0.565020862308762,-5.51953358362456,-2.55456319116061,1.81954393554187,0.95090772706677,0.57024632),
c("GO:0048646","anatomical structure formation involved in morphogenesis",4.59840055632823,6.87259846449514,-0.809409177198023,2.72427586960079,0.875861567765116,0.57050262),
c("GO:0048132","female germ-line stem cell asymmetric division",0.147774687065369,5.71430797539562,-0.41549290647552,1.25527250510331,0.866505886825998,0.57085562),
c("GO:0046039","GTP metabolic process",0.0434631432545202,-0.759168977834358,6.95743165290273,0.778151250383644,0.868343633298149,0.57116142),
c("GO:0097722","sperm motility",0.312934631432545,-3.46434292418258,2.15384672735117,1.56820172406699,0.900905289864943,0.57239225),
c("GO:0009615","response to virus",0.399860917941586,-6.48466238218413,-0.0692724895530893,1.67209785793572,0.948656298258089,0.57335996),
c("GO:0022603","regulation of anatomical structure morphogenesis",1.57336578581363,-2.41194995481488,-3.62736939135035,2.26007138798507,0.8871374941953,0.57456167),
c("GO:0032989","cellular component morphogenesis",4.59840055632823,6.36316756522692,1.12779591522277,2.72427586960079,0.805575627235683,0.57554006),
c("GO:0016043","cellular component organization",23.5048678720445,5.85494736904322,4.36377953080668,3.43216726944259,0.906728920532842,0.5756),
c("GO:0035825","homologous recombination",0.321627260083449,-1.98288504108385,6.61943344682252,1.57978359661681,0.887934821862876,0.57607228),
c("GO:0046700","heterocycle catabolic process",1.42559109874826,-2.25803779146858,6.34139074922994,2.21748394421391,0.88120829704033,0.57652295),
c("GO:0019932","second-messenger-mediated signaling",0.460709318497914,-5.37330317940392,-2.67230545597406,1.73239375982297,0.850453531887554,0.57688377),
c("GO:0007349","cellularization",0.99095966620306,6.61603842508472,-1.2797334217599,2.06069784035361,0.874423206481299,0.57715283),
c("GO:0035148","tube formation",0.382475660639778,6.87497856204946,-1.63519165657035,1.65321251377534,0.874114118772039,0.57715283),
c("GO:1901136","carbohydrate derivative catabolic process",0.695410292072323,-3.13063566021552,5.39252354920884,1.90848501887865,0.91796810416484,0.57716985),
c("GO:0071824","protein-DNA complex subunit organization",1.00834492350487,5.31087901244821,4.62214235066427,2.06818586174616,0.923976483088686,0.57718869),
c("GO:0070828","heterochromatin organization",0.843184979137691,5.52097743473557,4.50219752625918,1.99122607569249,0.917981470432119,0.57744917),
c("GO:0048645","animal organ formation",0.391168289290681,6.64939425652699,-1.46963474098353,1.66275783168157,0.867290398202377,0.57842968),
c("GO:0034968","histone lysine methylation",0.399860917941586,-2.71110345494895,6.10492922432092,1.67209785793572,0.906482445626471,0.57904117),
c("GO:0034599","cellular response to oxidative stress",0.339012517385257,-6.50287536782259,-1.11622327024237,1.60205999132796,0.912139875920128,0.57940336),
c("GO:0007399","nervous system development",9.17941585535466,6.25160211611068,-1.73250873814181,3.02407498730743,0.847904560203446,0.57944154),
c("GO:0032007","negative regulation of TOR signaling",0.139082058414465,-3.87715488045082,-6.07751528390528,1.23044892137827,0.884646062372123,0.58002694),
c("GO:0035330","regulation of hippo signaling",0.617176634214186,-3.75976566063268,-5.79920996054283,1.85733249643127,0.891537962767155,0.58002694),
c("GO:0019438","aromatic compound biosynthetic process",3.77260083449235,-1.46511173814699,6.06993026502463,2.63848925695464,0.865952471334887,0.58030603),
c("GO:0044267","cellular protein metabolic process",15.57719054242,-0.662933811011379,6.0255342159144,3.25358028956218,0.873659187542875,0.58040111),
c("GO:0099504","synaptic vesicle cycle",0.895340751043115,-5.45247934527979,3.07420090484051,2.01703333929878,0.911203376840624,0.58043448),
c("GO:0051641","cellular localization",9.02294853963839,-5.39183802119277,3.31767096059454,3.01661554755718,0.916590189067586,0.580436),
c("GO:0019439","aromatic compound catabolic process",1.52121001390821,-2.14836005294711,6.27542997958935,2.24551266781415,0.881061135133459,0.58096268),
c("GO:0045448","mitotic cell cycle, embryonic",0.252086230876217,5.29963248642964,-1.43002297178685,1.47712125471966,0.860838863853913,0.5814113),
c("GO:0009744","response to sucrose",0.182545201668985,-6.94197980963952,-0.451158618535537,1.34242268082221,0.942610150561851,0.58174998),
c("GO:0009167","purine ribonucleoside monophosphate metabolic process",0.208623087621697,-1.29815705656643,7.02330050309374,1.39794000867204,0.864146660401657,0.58199675),
c("GO:1902115","regulation of organelle assembly",0.269471488178025,-1.59744211323322,-4.66490964785521,1.50514997831991,0.887603595348347,0.58229906),
c("GO:0098659","inorganic cation import across plasma membrane",0.252086230876217,-5.47526051802201,2.97194737824197,1.47712125471966,0.927440559285029,0.5837683),
c("GO:0051169","nuclear transport",1.0691933240612,-5.73917747049367,3.16152946334495,2.09342168516224,0.915028188967986,0.5838844),
c("GO:0035218","leg disc development",0.843184979137691,6.55621280097204,-1.72857997293327,1.99122607569249,0.860281722024983,0.58433626),
c("GO:1905879","regulation of oogenesis",0.0173852573018081,-2.51837155271672,-1.25496518909096,0.477121254719662,0.910827480042482,0.58537357),
c("GO:0018130","heterocycle biosynthetic process",3.82475660639777,-1.57597396623545,6.05438968566105,2.64443858946784,0.865746926753388,0.58576843),
c("GO:0001666","response to hypoxia",0.512865090403338,-6.97205887480708,-1.17883838824716,1.77815125038364,0.945924394687998,0.58813195),
c("GO:0045815","epigenetic maintenance of chromatin in transcription-competent conformation",0.0782336578581363,2.03107072037492,-0.665536475636052,1,0.83544848099476,0.5884181),
c("GO:0006277","DNA amplification",0.191237830319889,-1.87921368827771,6.40980588632852,1.36172783601759,0.871190430905805,0.58845072),
c("GO:2000736","regulation of stem cell differentiation",0.286856745479833,-3.54429665510373,-3.49882730631698,1.53147891704226,0.894270481051765,0.58855491),
c("GO:0050890","cognition",1.39082058414465,5.73205088380029,-4.12189471765547,2.20682587603185,0.928400424721485,0.58911184),
c("GO:0097306","cellular response to alcohol",0.217315716272601,-6.45652703734149,-0.982566938539107,1.41497334797082,0.914387311001895,0.5903135),
c("GO:0031344","regulation of cell projection organization",1.26912378303199,-2.34866223732749,-5.71892885204271,2.16731733474818,0.878284264617878,0.59203685),
c("GO:0048194","Golgi vesicle budding",0.0173852573018081,3.27316939759273,4.34542834380414,0.477121254719662,0.904251711805074,0.59205801),
c("GO:0008407","chaeta morphogenesis",0.365090403337969,6.78028334712864,-1.63859133861974,1.63346845557959,0.870429930911015,0.59234849),
c("GO:0007099","centriole replication",0.217315716272601,5.29963973107808,4.08965187347489,1.41497334797082,0.895598418239529,0.59245123),
c("GO:0042386","hemocyte differentiation",0.252086230876217,6.00605482207113,-0.132826147663176,1.47712125471966,0.884704641211391,0.59371338),
c("GO:0070887","cellular response to chemical stimulus",3.71175243393602,-6.46996457501347,-1.12830157708927,2.63144376901317,0.904013640948971,0.59390552),
c("GO:0065004","protein-DNA complex assembly",0.617176634214186,5.36321307055871,4.65889665649345,1.85733249643127,0.917963914787785,0.59461455),
c("GO:0006516","glycoprotein catabolic process",0.0434631432545202,0.293784150409383,6.87999109919139,0.778151250383644,0.904257560371876,0.59465425),
c("GO:0018208","peptidyl-proline modification",0.53894297635605,-0.143234349629441,6.37706294869473,1.79934054945358,0.90632791103032,0.59522171),
c("GO:0002168","instar larval development",0.651947148817802,6.77482336078059,-2.1944723510647,1.88081359228079,0.888243628082133,0.5960837),
c("GO:0007166","cell surface receptor signaling pathway",3.57267037552156,-4.65372905987666,-3.05423017225679,2.61489721603313,0.820514119709645,0.59645461),
c("GO:0012502","induction of programmed cell death",0.121696801112656,1.0350805001818,-6.55789360784481,1.17609125905568,0.901692562918647,0.5979652),
c("GO:0050832","defense response to fungus",0.460709318497914,-6.26442925912149,-0.419877447245031,1.73239375982297,0.942793322407689,0.59815902),
c("GO:0060249","anatomical structure homeostasis",1.22566063977747,2.41620402316784,-5.64669797223804,2.15228834438306,0.896539127820365,0.59872795),
c("GO:0035304","regulation of protein dephosphorylation",0.278164116828929,-0.882168603924676,-6.8710291138824,1.51851393987789,0.880998091556962,0.59903298),
c("GO:0014070","response to organic cyclic compound",0.895340751043115,-6.73223606517682,-0.670841837371671,2.01703333929878,0.935446782093292,0.60058063),
c("GO:0046530","photoreceptor cell differentiation",1.66029207232267,6.19531415595265,-1.39932398339112,2.28330122870355,0.836430397552594,0.60122088),
c("GO:0097479","synaptic vesicle localization",0.226008344923505,-5.43988284238454,2.60820469072109,1.43136376415899,0.926991705749955,0.60127874),
c("GO:0019219","regulation of nucleobase-containing compound metabolic process",11.6568150208623,-1.46627687850785,-5.56876234002573,3.12775251583297,0.847673178915831,0.60134343),
c("GO:0048665","neuron fate specification",0.269471488178025,6.04875570731838,-1.13478616390868,1.50514997831991,0.856061456220024,0.60199794),
c("GO:0019538","protein metabolic process",20.1408205841446,-0.597180655255782,6.03863264745415,3.36511343162758,0.901606997075624,0.60267102),
c("GO:0035966","response to topologically incorrect protein",0.486787204450626,-6.74703077725314,-0.734856395465603,1.75587485567249,0.933575570494679,0.60275592),
c("GO:0071166","ribonucleoprotein complex localization",3.65742350486787,-5.63457878551777,3.01699152733744,2.62428209583567,0.911425190597462,0.60317134),
c("GO:0007379","segment specification",0.304242002781641,6.50503595190774,-2.66057055669066,1.55630250076729,0.898013776419724,0.60351325),
c("GO:0010160","formation of animal organ boundary",0.312934631432545,6.74536780003283,-1.73400086048214,1.56820172406699,0.863085490850868,0.60415854),
c("GO:0030258","lipid modification",0.686717663421419,1.7960245120789,6.8347670611237,1.90308998699194,0.91881520217123,0.60432361),
c("GO:0048523","negative regulation of cellular process",11.5872739916551,-2.036155283837,-5.04845731840697,3.12515582958053,0.852277777529001,0.60484234),
c("GO:0051338","regulation of transferase activity",1.13873435326843,2.07335619480113,-6.85855111765574,2.12057393120585,0.913955328894385,0.6056671),
c("GO:0007009","plasma membrane organization",0.234700973574409,6.39809540215622,4.33315343042477,1.44715803134222,0.937539386653562,0.60679052),
c("GO:0051784","negative regulation of nuclear division",0.191237830319889,-2.65247216578979,-5.98227562722446,1.36172783601759,0.870881797850507,0.60698093),
c("GO:0006221","pyrimidine nucleotide biosynthetic process",0.165159944367177,-1.08714835527568,6.59167568061192,1.30102999566398,0.849369365877115,0.60818303),
c("GO:0034249","negative regulation of cellular amide metabolic process",0.756258692628651,-1.61477538317397,-6.23503902793116,1.94448267215017,0.861910465925413,0.60826583),
c("GO:0007275","multicellular organism development",20.0712795549374,6.10156459657425,-1.65289025817153,3.36361197989214,0.861589736478871,0.60862563),
c("GO:0007007","inner mitochondrial membrane organization",0.243393602225313,5.45502169369781,5.17316389852406,1.46239799789896,0.928391804460343,0.60862927),
c("GO:0000278","mitotic cell cycle",3.46835883171071,2.26450103396496,-1.06459230535354,2.60205999132796,0.940161268218785,0.60874611),
c("GO:0034440","lipid oxidation",0.339012517385257,2.15681122858858,6.74756992176664,1.60205999132796,0.923225592516661,0.60885794),
c("GO:0035172","hemocyte proliferation",0.0521557719054242,4.48127779318577,-6.41596458605865,0.845098040014257,0.964257626820396,0.60921207),
c("GO:0030537","larval behavior",0.443324061196106,5.274582736561,-4.32342456156265,1.7160033436348,0.933989899042981,0.60969721),
c("GO:0010324","membrane invagination",0.252086230876217,6.4408172741846,4.19407637865824,1.47712125471966,0.938213474163791,0.61041408),
c("GO:0009620","response to fungus",0.573713490959666,-6.40713085759594,-0.174239252670432,1.82607480270083,0.94693069540592,0.61109381),
c("GO:0008154","actin polymerization or depolymerization",0.199930458970793,5.0633892837365,5.1696383165307,1.38021124171161,0.921310819602554,0.61173077),
c("GO:0009072","aromatic amino acid family metabolic process",0.165159944367177,-0.794423576212664,7.11721757066473,1.30102999566398,0.885687846065689,0.61177456),
c("GO:0032506","cytokinetic process",0.339012517385257,2.3605400841813,0.029981246149565,1.60205999132796,0.946380327557861,0.6132263),
c("GO:0033047","regulation of mitotic sister chromatid segregation",0.156467315716273,-0.0856989509533493,-6.42837506219728,1.27875360095283,0.879272572133937,0.61330792),
c("GO:0006360","transcription by RNA polymerase I",0.147774687065369,-1.88423648539604,6.47056181779443,1.25527250510331,0.873976199774977,0.61334176),
c("GO:0050921","positive regulation of chemotaxis",0.0260778859527121,1.00690999667581,-4.87621665261687,0.602059991327962,0.900602103456113,0.6138373),
c("GO:0002252","immune effector process",0.373783031988873,4.48514291794359,-6.51206243947967,1.64345267648619,0.983811051054787,0.6145457),
c("GO:0015698","inorganic anion transport",0.651947148817802,-5.84358306657252,3.58748848546628,1.88081359228079,0.941602573301631,0.61518322),
c("GO:1902531","regulation of intracellular signal transduction",3.05111265646732,-3.09032613528339,-5.50254842262539,2.54654266347813,0.873939238744307,0.6151882),
c("GO:0000041","transition metal ion transport",0.382475660639778,-5.82282878940699,3.70861217911221,1.65321251377534,0.944413959840588,0.61581401),
c("GO:0006826","iron ion transport",0.147774687065369,-5.96044993711873,3.72803159075491,1.25527250510331,0.948871758804784,0.61581401),
c("GO:0034620","cellular response to unfolded protein",0.330319888734353,-6.53974574097773,-1.03572993108894,1.5910646070265,0.906510360981564,0.61603719),
c("GO:0070252","actin-mediated cell contraction",0.217315716272601,1.62563837610222,2.61694178731215,1.41497334797082,0.957931661963601,0.61603719),
c("GO:1900180","regulation of protein localization to nucleus",0.121696801112656,-0.838667601833379,-2.48865112742981,1.17609125905568,0.90699745204499,0.61683971),
c("GO:0120032","regulation of plasma membrane bounded cell projection assembly",0.425938803894298,-2.54826580431455,-5.83987754396192,1.69897000433602,0.882785224004059,0.61767345),
c("GO:0051783","regulation of nuclear division",0.530250347705146,-2.73650760134448,-5.85451247526537,1.79239168949825,0.883892639876713,0.61782886),
c("GO:0006811","ion transport",5.34596662030598,-5.4646593960945,3.38972935036598,2.78958071216443,0.937655182638088,0.61796686),
c("GO:0090659","walking behavior",0.13038942976356,2.88788039566579,-3.7938827000772,1.20411998265592,0.987071828201459,0.61825121),
c("GO:0030308","negative regulation of cell growth",0.208623087621697,-2.31116701636469,-5.84918665554614,1.39794000867204,0.872987911623581,0.61827838),
c("GO:0016042","lipid catabolic process",1.2865090403338,1.3009405239825,6.43278619478791,2.17318626841227,0.916713326049214,0.62033237),
c("GO:0043523","regulation of neuron apoptotic process",0.191237830319889,0.912903500730771,-6.52922623045898,1.36172783601759,0.918112848666695,0.62068417),
c("GO:1901654","response to ketone",0.391168289290681,-6.72674961634044,-0.560958195639563,1.66275783168157,0.939089090809121,0.6211378),
c("GO:0001578","microtubule bundle formation",0.608484005563282,5.36656037949905,4.89815504997787,1.85125834871908,0.915149983134214,0.62152973),
c("GO:0070482","response to oxygen levels",0.62586926286509,-6.33957428264468,-0.772347445593305,1.86332286012046,0.952758603196302,0.6215432),
c("GO:0048468","cell development",11.5698887343533,6.59526867288074,-0.696893309542922,3.12450422483428,0.840268334026788,0.62163504),
c("GO:0030148","sphingolipid biosynthetic process",0.425938803894298,0.292034677550625,6.15823125080167,1.69897000433602,0.886464882027154,0.62217039),
c("GO:0012501","programmed cell death",1.60813630041725,0.0650271303849635,1.67051777845636,2.26951294421792,0.966889427532835,0.62275149),
c("GO:0051402","neuron apoptotic process",0.0173852573018081,-1.34324191107541,1.29644168380473,0.477121254719662,0.977192006560742,0.62275149),
c("GO:1902806","regulation of cell cycle G1/S phase transition",0.191237830319889,-3.61889713607645,-2.86417863547056,1.36172783601759,0.907202442608865,0.62302516),
c("GO:0044092","negative regulation of molecular function",1.75591098748261,1.74486452451383,-6.67586291608488,2.30749603791321,0.910914803260707,0.62335047),
c("GO:0048545","response to steroid hormone",0.13038942976356,-6.95925990615725,-0.371521286389795,1.20411998265592,0.940544341666871,0.62358698),
c("GO:0046068","cGMP metabolic process",0.139082058414465,-0.795133304313365,6.78899843173181,1.23044892137827,0.858184871069343,0.62359517),
c("GO:0044719","regulation of imaginal disc-derived wing size",0.113004172461752,5.39149437387602,-2.48429383701706,1.14612803567824,0.795094914697641,0.62364119),
c("GO:0031532","actin cytoskeleton reorganization",0.252086230876217,5.10685521492721,5.09282893496789,1.47712125471966,0.921200486943397,0.62385457),
c("GO:0072553","terminal button organization",0.113004172461752,5.23190517149872,4.02523661446229,1.14612803567824,0.941990236681363,0.62432112),
c("GO:0048568","embryonic organ development",0.512865090403338,6.28565497103325,-2.33996481117051,1.77815125038364,0.875446002729683,0.62482694),
c("GO:0042593","glucose homeostasis",0.399860917941586,3.12400616843929,-6.00386040440332,1.67209785793572,0.905136477662553,0.62515419),
c("GO:0006996","organelle organization",15.2642559109875,5.84000557851613,4.38417556119964,3.24477176149529,0.908805033109845,0.62536225),
c("GO:0007293","germarium-derived egg chamber formation",0.843184979137691,6.17306744309397,-0.749952005806177,1.99122607569249,0.834060768064724,0.62574197),
c("GO:0002009","morphogenesis of an epithelium",4.99826147426982,6.86858954783545,-0.898263695394289,2.76042248342321,0.856169854962392,0.62601087),
c("GO:0050953","sensory perception of light stimulus",0.599791376912378,5.72612536738574,-4.37456700300328,1.84509804001426,0.933483916780307,0.62626467),
c("GO:1904748","regulation of apoptotic process involved in development",0.113004172461752,-3.15720798180808,-2.84773149558582,1.14612803567824,0.900470746453848,0.62654754),
c("GO:0071897","DNA biosynthetic process",0.399860917941586,-1.71677689381257,6.3408918930753,1.67209785793572,0.863254658386349,0.62699326),
c("GO:0099003","vesicle-mediated transport in synapse",0.90403337969402,-5.16800447476675,3.16722786590402,2.02118929906994,0.9214682472928,0.62806731),
c("GO:0002230","positive regulation of defense response to virus by host",0.104311543810848,0.984082379578106,-7.47696683607888,1.11394335230684,0.911202265083045,0.62818271),
c("GO:1902692","regulation of neuroblast proliferation",0.399860917941586,-3.07633982734125,-3.47177209100157,1.67209785793572,0.91434772332682,0.62818921),
c("GO:0007188","adenylate cyclase-modulating G protein-coupled receptor signaling pathway",0.565020862308762,-5.28752191704288,-2.73993671812829,1.81954393554187,0.850692056405557,0.62880534),
c("GO:0035203","regulation of lamellocyte differentiation",0.0956189151599444,-1.38815866261622,-2.91757775324474,1.07918124604762,0.892567657589091,0.62928878),
c("GO:0090175","regulation of establishment of planar polarity",0.165159944367177,-2.73851187218521,-2.11171465648745,1.30102999566398,0.905239123667708,0.62949288),
c("GO:0048731","system development",14.7166203059805,6.17298243292314,-1.74054877609393,3.22891340599469,0.855540727464374,0.62965645),
c("GO:0060341","regulation of cellular localization",1.04311543810848,-2.99715986331783,-4.28594842045601,2.08278537031645,0.891353586593296,0.63005159),
c("GO:0042048","olfactory behavior",0.608484005563282,-6.03200639926482,-0.833357791084339,1.85125834871908,0.933008349102573,0.63047256),
c("GO:0035287","head segmentation",0.182545201668985,6.43245371463912,-2.71905864930628,1.34242268082221,0.89570510678465,0.6314229),
c("GO:0090304","nucleic acid metabolic process",10.0052155771905,-1.1669880220354,6.28330133079936,3.06145247908719,0.854808542440113,0.6314729),
c("GO:0071705","nitrogen compound transport",5.94575799721836,-5.46771190423656,3.24260777781824,2.83569057149243,0.936822625707823,0.63219773),
c("GO:0009187","cyclic nucleotide metabolic process",0.269471488178025,-1.30359866654466,6.96170247986011,1.50514997831991,0.863249329152962,0.6328119),
c("GO:1903706","regulation of hemopoiesis",0.104311543810848,-2.45988152728411,-1.97983398334124,1.11394335230684,0.90026113669292,0.63390085),
c("GO:0048569","post-embryonic animal organ development",3.90299026425591,6.31427586637931,-1.87103499744204,2.65321251377534,0.853890368087679,0.63396042),
c("GO:0034504","protein localization to nucleus",0.49547983310153,-5.90165700986539,2.90053206798867,1.76342799356294,0.921019113772676,0.63519476),
c("GO:0008380","RNA splicing",2.06015299026426,-1.51364073227273,6.45823419414385,2.37657695705651,0.871051802267603,0.63580138),
c("GO:0042136","neurotransmitter biosynthetic process",0.0695410292072323,-3.3614293516204,4.35769824198179,0.954242509439325,0.852977785033645,0.63639481),
c("GO:0051270","regulation of cellular component movement",1.04311543810848,-3.07925248047197,-4.31322417347064,2.08278537031645,0.891353586593296,0.63668935),
c("GO:0010468","regulation of gene expression",14.8383171070932,-1.2778385680661,-5.60281946109651,3.23248786635299,0.852195792464277,0.63783868),
c("GO:0043269","regulation of ion transport",0.782336578581363,-0.279251698963692,-4.08224113293989,1.95904139232109,0.897080739845136,0.63836697),
c("GO:0071826","ribonucleoprotein complex subunit organization",1.19958275382476,5.37049404932447,4.58273896896737,2.14301480025409,0.922633920253415,0.63842417),
c("GO:0035285","appendage segmentation",0.208623087621697,6.7641962208042,-2.30259849734412,1.39794000867204,0.884210987296527,0.63846821),
c("GO:0007264","small GTPase mediated signal transduction",0.895340751043115,-5.12943254838558,-2.77709740298663,2.01703333929878,0.840780108502393,0.63856016),
c("GO:0035493","SNARE complex assembly",0.0173852573018081,3.62727088807753,4.47378979399224,0.477121254719662,0.893243563652854,0.63892882),
c("GO:0009057","macromolecule catabolic process",4.35500695410292,-1.93658395189279,5.43308308234634,2.70070371714502,0.912396727182566,0.63927355),
c("GO:0050954","sensory perception of mechanical stimulus",0.712795549374131,5.72695891753459,-4.31191591942306,1.91907809237607,0.932348925217546,0.63977747),
c("GO:0007169","transmembrane receptor protein tyrosine kinase signaling pathway",1.086578581363,-5.0643897497667,-2.8253898325164,2.10037054511756,0.837027728473152,0.64112551),
c("GO:0033554","cellular response to stress",4.87656467315716,-6.50820197705686,-1.40990110859307,2.74973631556906,0.908441180359139,0.64113179),
c("GO:0006517","protein deglycosylation",0.121696801112656,0.172708637062677,6.9307679833743,1.17609125905568,0.906116481584348,0.64113863),
c("GO:0007635","chemosensory behavior",0.712795549374131,-6.04873840827961,-0.87762747205497,1.91907809237607,0.932362802219373,0.64139259),
c("GO:0051306","mitotic sister chromatid separation",0.0434631432545202,5.43810999167143,3.69526122038449,0.778151250383644,0.916765875324337,0.64157007),
c("GO:0016310","phosphorylation",3.39881780250348,-0.190604327224056,5.55021400335432,2.59328606702046,0.889083088828958,0.64158993),
c("GO:0030703","eggshell formation",1.0691933240612,6.18265945712017,-0.795969998812123,2.09342168516224,0.830078270174538,0.64197762),
c("GO:0006998","nuclear envelope organization",0.147774687065369,5.32234610818976,5.3074463844495,1.25527250510331,0.931454975752698,0.64201432),
c("GO:0048867","stem cell fate determination",0.00869262865090403,5.56484970022561,0.425296657843628,0.301029995663981,0.913083220321718,0.64206509),
c("GO:0070507","regulation of microtubule cytoskeleton organization",0.443324061196106,-4.27925491923527,-5.06264584633219,1.7160033436348,0.883624944593916,0.64306314),
c("GO:0016071","mRNA metabolic process",3.09457579972184,-1.42686968014864,6.40375524172648,2.55266821611219,0.869217855995993,0.64388259),
c("GO:0009312","oligosaccharide biosynthetic process",0.165159944367177,2.14601501986862,6.17901492575742,1.30102999566398,0.931283415993595,0.64404144),
c("GO:0007354","zygotic determination of anterior/posterior axis, embryo",0.208623087621697,6.45883285660135,-2.68327191994566,1.39794000867204,0.895211115622647,0.64418595),
c("GO:0048871","multicellular organismal homeostasis",0.643254520166898,4.0273676686856,-4.40188266238792,1.8750612633917,0.850421113678496,0.64438922),
c("GO:0030031","cell projection assembly",1.56467315716273,5.9201082562269,4.24988066470318,2.25767857486918,0.909214663176898,0.64609761),
c("GO:0043086","negative regulation of catalytic activity",1.46036161335188,1.96583232893324,-6.90890912367952,2.22788670461367,0.910282863126656,0.64682784),
c("GO:2000027","regulation of animal organ morphogenesis",0.199930458970793,-2.80220780380678,-2.28008870253191,1.38021124171161,0.904327690901644,0.64759343),
c("GO:0007097","nuclear migration",0.286856745479833,-5.96945393433013,3.12033654625246,1.53147891704226,0.920312624267446,0.64816576),
c("GO:0061025","membrane fusion",0.512865090403338,5.11394551164696,4.44711375645936,1.77815125038364,0.934114518362123,0.64893033),
c("GO:0048193","Golgi vesicle transport",1.21696801112656,-5.36748480090187,3.40392177689151,2.14921911265538,0.919085686804646,0.64921543),
c("GO:0007369","gastrulation",0.738873435326843,6.58421189459156,-1.41737276179286,1.93449845124357,0.875754198010062,0.6497697),
c("GO:0031122","cytoplasmic microtubule organization",0.269471488178025,5.20575626740674,5.10637416675718,1.50514997831991,0.919516740169689,0.65044944),
c("GO:2001233","regulation of apoptotic signaling pathway",0.182545201668985,-4.45855523635464,-5.59921531483407,1.34242268082221,0.89776034210784,0.65046058),
c("GO:0006399","tRNA metabolic process",1.26043115438108,-1.61874772725448,6.56834943078778,2.16435285578444,0.879289751705313,0.65052206),
c("GO:0033500","carbohydrate homeostasis",0.478094575799722,3.05289325481942,-6.03507393385934,1.7481880270062,0.903555605905035,0.65116084),
c("GO:0002793","positive regulation of peptide secretion",0.0782336578581363,2.16961123722448,-6.45075856018252,1,0.897093466338665,0.65194573),
c("GO:0006974","cellular response to DNA damage stimulus",2.1470792767733,-6.53778383390527,-1.48370516759297,2.39445168082622,0.913097943601479,0.65326836),
c("GO:1900182","positive regulation of protein localization to nucleus",0.0608484005563282,-0.135833915899617,-2.74629559278817,0.903089986991944,0.894641995516533,0.65386503),
c("GO:0008586","imaginal disc-derived wing vein morphogenesis",0.373783031988873,6.75656868576425,-1.53858162459075,1.64345267648619,0.853035788402097,0.65473293),
c("GO:1902600","proton transmembrane transport",0.782336578581363,-5.39212851389087,3.14960962068497,1.95904139232109,0.919803965603396,0.6549898),
c("GO:1901361","organic cyclic compound catabolic process",1.55598052851182,-2.40917156329627,6.43368845097224,2.25527250510331,0.898824031774552,0.65593443),
c("GO:0016055","Wnt signaling pathway",0.504172461752434,-5.31021454421999,-2.63315015736255,1.77085201164214,0.845599152043941,0.6560898),
c("GO:0048585","negative regulation of response to stimulus",3.52920723226704,-2.76404704453655,-5.50789872237486,2.60959440922522,0.858499603432004,0.65705646),
c("GO:0010557","positive regulation of macromolecule biosynthetic process",4.80702364394993,-0.912591050358722,-5.77868966085486,2.74350976472843,0.840657604260095,0.65869548),
c("GO:0007165","signal transduction",10.7527816411683,-4.30015904980572,-3.25817183884945,3.0927206446841,0.796326277299233,0.6588474),
c("GO:0001708","cell fate specification",0.747566063977747,6.72500294982716,0.00940758712860967,1.93951925261862,0.878460963040985,0.65929679),
c("GO:0007265","Ras protein signal transduction",0.634561891515994,-5.23368631757686,-2.70312733921338,1.86923171973098,0.845707911464058,0.65947385),
c("GO:0055076","transition metal ion homeostasis",0.460709318497914,2.93961517970872,-5.79474915418788,1.73239375982297,0.901854827754502,0.65976244),
c("GO:0007448","anterior/posterior pattern specification, imaginal disc",0.226008344923505,6.74928851848763,-2.06250975477821,1.43136376415899,0.869808452293121,0.66081751),
c("GO:0060581","cell fate commitment involved in pattern specification",0.304242002781641,6.05145513427581,-1.12533991897299,1.55630250076729,0.865267600988423,0.66108437),
c("GO:0010927","cellular component assembly involved in morphogenesis",1.2952016689847,6.35523326498624,1.28718557526884,2.17609125905568,0.810977063840172,0.661324),
c("GO:0035721","intraciliary retrograde transport",0.0608484005563282,2.9937754422188,4.03813910592057,0.903089986991944,0.875677184111322,0.66132971),
c("GO:0009141","nucleoside triphosphate metabolic process",0.356397774687065,-1.27171955386774,6.89664792428377,1.6232492903979,0.85992280216141,0.66214387),
c("GO:0045216","cell-cell junction organization",0.660639777468707,6.15195254672595,3.97369038360463,1.88649072517248,0.932390515736791,0.66221986),
c("GO:0055085","transmembrane transport",7.34527121001391,-5.54064300916431,3.26722349432207,2.92737036303902,0.909803801741912,0.66252629),
c("GO:0033044","regulation of chromosome organization",0.608484005563282,-2.57925979513882,-6.21024715633269,1.85125834871908,0.882389699821064,0.66275448),
c("GO:0008345","larval locomotory behavior",0.304242002781641,5.23709261419351,-4.43964432906937,1.55630250076729,0.935241080464185,0.66379877),
c("GO:0030166","proteoglycan biosynthetic process",0.191237830319889,-0.40588963743124,5.79191212682959,1.36172783601759,0.885846041189377,0.6639214),
c("GO:0006412","translation",2.76425591098748,-1.05667229274046,6.15673301995786,2.50379068305718,0.843919801065154,0.66480838),
c("GO:0071702","organic substance transport",7.49304589707928,-5.50914683288693,3.2347143345096,2.93601079571521,0.934931170114478,0.66553492),
c("GO:0000910","cytokinesis",0.817107093184979,2.99864911048866,-3.46278566942773,1.97772360528885,0.943327855040045,0.66556467),
c("GO:0000027","ribosomal large subunit assembly",0.139082058414465,5.36191389689098,5.00552358797945,1.23044892137827,0.916509523257618,0.66585311),
c("GO:0007346","regulation of mitotic cell cycle",1.46905424200278,-4.01967910402588,-4.74517312612324,2.23044892137827,0.891450566973339,0.66588165),
c("GO:0048813","dendrite morphogenesis",1.15611961057024,6.27344054448605,0.720783693631763,2.12710479836481,0.793415793938204,0.66719372),
c("GO:0035289","posterior head segmentation",0.113004172461752,6.49623256261309,-2.7977641690796,1.14612803567824,0.899827453668639,0.66763326),
c("GO:0007032","endosome organization",0.243393602225313,5.40731925066991,5.26932025651952,1.46239799789896,0.930400277539218,0.66854983),
c("GO:0033043","regulation of organelle organization",2.92941585535466,-2.146990691444,-5.39576963537664,2.52891670027765,0.86692760575299,0.66944798),
c("GO:0009166","nucleotide catabolic process",0.165159944367177,-1.22154195520779,6.81614267947202,1.30102999566398,0.856652489368168,0.67048575),
c("GO:0008587","imaginal disc-derived wing margin morphogenesis",0.45201668984701,6.71321872615519,-1.53527839665039,1.72427586960079,0.850446461095564,0.67122835),
c("GO:0007617","mating behavior",1.0778859527121,4.98848250476355,-3.35641263826493,2.09691001300806,0.902968235571428,0.67180638),
c("GO:0006643","membrane lipid metabolic process",0.921418636995827,1.65255728623103,6.79451603473553,2.02938377768521,0.916393604083546,0.67182675),
c("GO:0051647","nucleus localization",0.347705146036161,-5.76151076598035,2.77457255464283,1.61278385671974,0.925707182073055,0.67241294),
c("GO:0061245","establishment or maintenance of bipolar cell polarity",0.295549374130737,-1.49248355429641,0.958597617783391,1.54406804435028,0.974835917221989,0.6727402),
c("GO:0045664","regulation of neuron differentiation",0.695410292072323,-3.2504466438039,-3.72958146237576,1.90848501887865,0.885355381820721,0.67278434),
c("GO:0046578","regulation of Ras protein signal transduction",0.695410292072323,-3.77165334517383,-5.7162821942115,1.90848501887865,0.889513145456857,0.67285703),
c("GO:0044242","cellular lipid catabolic process",0.704102920723227,-2.88326860213229,5.48710031475081,1.91381385238372,0.90202947204115,0.67356859),
c("GO:0051129","negative regulation of cellular component organization",1.34735744089013,-2.38262329517912,-5.41624184288005,2.19312459835446,0.855395320415794,0.67455751),
c("GO:0035317","imaginal disc-derived wing hair organization",0.399860917941586,6.33492588373745,0.61795359114201,1.67209785793572,0.788835190716499,0.67537343),
c("GO:0031023","microtubule organizing center organization",0.669332406119611,5.33921451300784,4.86751408484025,1.89209460269048,0.91438076655073,0.67551805),
c("GO:0009266","response to temperature stimulus",1.17350486787204,-6.99201296823521,-1.12512463851571,2.13353890837022,0.949781815767814,0.67559055),
c("GO:0045610","regulation of hemocyte differentiation",0.217315716272601,-3.22390457025872,-3.28169030294815,1.41497334797082,0.887280362419717,0.67567267),
c("GO:0010648","negative regulation of cell communication",3.30319888734353,-2.85510769803573,-5.36279390532724,2.58092497567562,0.858179216911711,0.67577411),
c("GO:0023057","negative regulation of signaling",3.31189151599444,-2.97530969475885,-5.54495956796307,2.58206336291171,0.866046220114659,0.6760316),
c("GO:0019098","reproductive behavior",1.13873435326843,5.1384061778044,-3.50136650972231,2.12057393120585,0.902851569993896,0.67606325),
c("GO:0050807","regulation of synapse organization",1.37343532684284,-0.583902572760366,-5.11774451517188,2.20139712432045,0.855500287944218,0.67621149),
c("GO:0040018","positive regulation of multicellular organism growth",0.217315716272601,-0.653547549858377,-3.37519354446681,1.41497334797082,0.878575759306938,0.67641286),
c("GO:0044093","positive regulation of molecular function",2.22531293463143,1.51290291034786,-6.41657262250751,2.40993312333129,0.908567320196576,0.67656931),
c("GO:0042693","muscle cell fate commitment",0.121696801112656,6.98282066658219,0.309449136196572,1.17609125905568,0.888906905294258,0.67690563),
c("GO:0022607","cellular component assembly",9.87482614742698,5.79868126556831,4.45130374450002,3.05576046468773,0.901626440722226,0.67707058),
c("GO:0031399","regulation of protein modification process",2.06015299026426,-1.30850580848423,-6.0955421250001,2.37657695705651,0.865058771899489,0.6771686),
c("GO:0019752","carboxylic acid metabolic process",3.32058414464534,0.0334830152234245,6.21958749284304,2.58319877396862,0.874970857610045,0.67827183),
c("GO:0009132","nucleoside diphosphate metabolic process",0.356397774687065,-1.24253125298927,6.89559990683949,1.6232492903979,0.85992280216141,0.67856479),
c("GO:0042176","regulation of protein catabolic process",0.930111265646732,-0.741629233616912,-6.6301593357668,2.03342375548695,0.873899886005036,0.67911141),
c("GO:0007447","imaginal disc pattern formation",0.930111265646732,6.58902026412546,-1.85771836278517,2.03342375548695,0.852870287516289,0.67915068),
c("GO:0071103","DNA conformation change",1.95584144645341,5.58034229206264,4.50259198216499,2.3541084391474,0.911645088713164,0.67987073),
c("GO:0006468","protein phosphorylation",2.26877607788595,-0.6014932517028,6.20928365017916,2.41830129131975,0.867506070694586,0.67987445),
c("GO:0044273","sulfur compound catabolic process",0.113004172461752,0.881343546753401,4.35738309227475,1.14612803567824,0.925129736043494,0.6807328),
c("GO:0035303","regulation of dephosphorylation",0.339012517385257,-1.0982262778661,-6.85142588378323,1.60205999132796,0.889429907924675,0.68103892),
c("GO:2000026","regulation of multicellular organismal development",2.39916550764951,-2.28704911616607,-3.81317767390498,2.44247976906445,0.877679081788721,0.68109958),
c("GO:0035239","tube morphogenesis",4.3115438108484,6.46437676536725,-1.5799231645251,2.69635638873333,0.846910937467598,0.68118368),
c("GO:0034332","adherens junction organization",0.252086230876217,6.4940609721712,3.92149610633562,1.47712125471966,0.937909963397463,0.68164633),
c("GO:0009582","detection of abiotic stimulus",0.686717663421419,-7.08999791356717,-0.978340843951342,1.90308998699194,0.949651928989207,0.68224038),
c("GO:2000116","regulation of cysteine-type endopeptidase activity",0.278164116828929,0.274406821522474,-6.82572354966728,1.51851393987789,0.881474916003109,0.68249091),
c("GO:0043085","positive regulation of catalytic activity",1.79937413073713,1.72154570440955,-6.69300368093284,2.31806333496276,0.90754173159758,0.68272422),
c("GO:0009123","nucleoside monophosphate metabolic process",0.382475660639778,-1.27855329799815,6.86271995275346,1.65321251377534,0.859038756935246,0.68284203),
c("GO:0007193","adenylate cyclase-inhibiting G protein-coupled receptor signaling pathway",0.208623087621697,-5.66815105478935,-2.56216355505436,1.39794000867204,0.863381846164358,0.68315198),
c("GO:0007474","imaginal disc-derived wing vein specification",0.460709318497914,6.68814122056394,-1.70822869759117,1.73239375982297,0.845370676256293,0.68424844),
c("GO:0009887","animal organ morphogenesis",6.2413073713491,6.36393856541277,-1.60098022734828,2.85672889038288,0.834693127759931,0.68436147),
c("GO:0043406","positive regulation of MAP kinase activity",0.0173852573018081,-0.275966719160601,-6.75587404328229,0.477121254719662,0.86407696055876,0.68511808),
c("GO:0051234","establishment of localization",17.1679415855355,-5.51076495822916,3.29234701530188,3.29578694025161,0.937301131204133,0.68540035),
c("GO:0009408","response to heat",0.721488178025035,-6.93121933052054,-1.1414383233526,1.92427928606188,0.945340572903187,0.68583412),
c("GO:0034762","regulation of transmembrane transport",0.521557719054242,-0.891071333233203,-3.95039640891446,1.78532983501077,0.895621124943208,0.68650562),
c("GO:0051056","regulation of small GTPase mediated signal transduction",0.764951321279555,-3.70593870393844,-5.7082942263252,1.94939000664491,0.889271472116731,0.68753293),
c("GO:0033108","mitochondrial respiratory chain complex assembly",0.58240611961057,5.47476666687258,4.78248346377814,1.83250891270624,0.911602639814495,0.68770336),
c("GO:0046777","protein autophosphorylation",0.330319888734353,-0.432297573557641,6.30555167865011,1.5910646070265,0.890375154797403,0.6878354),
c("GO:0035268","protein mannosylation",0.113004172461752,-0.577825640417502,5.49311649962616,1.14612803567824,0.885621857012102,0.68784549),
c("GO:1902850","microtubule cytoskeleton organization involved in mitosis",0.730180806675939,5.31203000329711,3.98515991700243,1.92941892571429,0.892180497970645,0.68792567),
c("GO:0055088","lipid homeostasis",0.721488178025035,2.73463232397821,-5.75058456312976,1.92427928606188,0.899704010453463,0.68856472),
c("GO:0006817","phosphate ion transport",0.182545201668985,-5.92261498175804,3.77237555844404,1.34242268082221,0.947803123581583,0.68885629),
c("GO:0006084","acetyl-CoA metabolic process",0.13038942976356,-0.757708818721776,6.68827714515415,1.20411998265592,0.853134696247308,0.68888469),
c("GO:0040005","chitin-based cuticle attachment to epithelium",0.0260778859527121,5.3728517755062,-5.41883376747282,0.602059991327962,0.955076756213338,0.68900849),
c("GO:0051171","regulation of nitrogen compound metabolic process",17.0114742698192,-1.30163350845782,-5.56273058425278,3.29181268746712,0.851725119339906,0.68934341),
c("GO:0097305","response to alcohol",1.00834492350487,-6.6752732188661,-0.704292944697462,2.06818586174616,0.933483901486112,0.6894956),
c("GO:0030534","adult behavior",1.35605006954103,5.36829914105047,-4.0194724690712,2.19589965240923,0.926234410204722,0.68996816),
c("GO:0007446","imaginal disc growth",0.104311543810848,6.85365409941747,-2.18199795003982,1.11394335230684,0.879462199968736,0.69007714),
c("GO:0048856","anatomical structure development",23.4787899860918,6.72009081464742,-0.877179676734957,3.43168534468601,0.878360469713946,0.69023619),
c("GO:0051093","negative regulation of developmental process",1.76460361613352,-2.42886445331523,-3.90929060537302,2.3096301674259,0.863087482297199,0.6911582),
c("GO:0007611","learning or memory",1.38212795549374,5.43128402246783,-4.0940353408564,2.20411998265592,0.917528555264473,0.69151929),
c("GO:0032204","regulation of telomere maintenance",0.0260778859527121,-0.119275187555418,-7.11145381519217,0.602059991327962,0.885265779205036,0.69170405),
c("GO:0046532","regulation of photoreceptor cell differentiation",0.391168289290681,-3.63266247716858,-3.70092874685764,1.66275783168157,0.889667161863696,0.69263434),
c("GO:0030720","oocyte localization involved in germarium-derived egg chamber formation",0.121696801112656,4.53448080455086,-0.278080311995326,1.17609125905568,0.826801542269396,0.69313363),
c("GO:0043254","regulation of protein-containing complex assembly",0.930111265646732,-2.42780619711725,-5.9067291809274,2.03342375548695,0.878102558908368,0.69316484),
c("GO:0009712","catechol-containing compound metabolic process",0.13038942976356,-1.70321066631414,7.51045395713643,1.20411998265592,0.91279207601548,0.69345187),
c("GO:0007480","imaginal disc-derived leg morphogenesis",0.608484005563282,6.64535910846909,-1.54444652761624,1.85125834871908,0.845797464272773,0.69413115),
c("GO:1901137","carbohydrate derivative biosynthetic process",2.79033379694019,-0.776454799766698,5.04009882270415,2.50785587169583,0.89606366937276,0.69629217),
c("GO:0006816","calcium ion transport",0.599791376912378,-5.88187014012674,3.58913650609777,1.84509804001426,0.94201925425734,0.6965705),
c("GO:1905475","regulation of protein localization to membrane",0.147774687065369,-0.996578277946252,-2.59087624237319,1.25527250510331,0.905500778000198,0.69772267),
c("GO:0001676","long-chain fatty acid metabolic process",0.243393602225313,1.5959778227204,7.07571304680572,1.46239799789896,0.891650956013127,0.69808835),
c("GO:0006935","chemotaxis",2.3730876216968,-6.51516423220186,-0.562614006295983,2.43775056282039,0.917487294461467,0.69814508),
c("GO:0010721","negative regulation of cell development",0.40855354659249,-2.83726651085668,-3.66174122197505,1.68124123737559,0.866197004147878,0.69837705),
c("GO:0048513","animal organ development",10.1182197496523,6.25596195529008,-1.76362272938944,3.06632592536204,0.845885123995565,0.69851688),
c("GO:0055086","nucleobase-containing small molecule metabolic process",2.45132127955494,-1.15482018187489,6.55920079510289,2.45178643552429,0.859427716718929,0.69895846),
c("GO:0035265","organ growth",0.121696801112656,6.28607425130819,-3.36043102447129,1.17609125905568,0.919707060152905,0.69912442));
```

```{r plot save REVIGO, eval = TRUE, echo = FALSE, include = TRUE}

one.data                <- data.frame(revigo.data, stringsAsFactors = FALSE)
names(one.data)         <- revigo.names
one.data                <- one.data [(one.data$plot_X != "null" & one.data$plot_Y != "null"), ]
one.data$plot_X         <- as.numeric( as.character(one.data$plot_X) )
one.data$plot_Y         <- as.numeric( as.character(one.data$plot_Y) )
one.data$log_size      <- as.numeric( as.character(one.data$log_size) )
#one.data$frequency      <- as.numeric( as.character(one.data$frequency) )
one.data$uniqueness     <- as.numeric( as.character(one.data$uniqueness) )
one.data$dispensability <- as.numeric( as.character(one.data$dispensability) )
#head(one.data)


# object taken from TopGO analysis
# a list of 9980 drosophila genes, with associated GO Terms for BP
# obtained from this script: 2021-05-14-svm-result-analysis.Rmd
#gene2go

# a dataframe with the droso gene names for those 127 predictor genes
# obtained from this script: 2021-05-14-svm-result-analysis.Rmd
#raw_selectionGenes#

# subset gene2go for only those 127 predictor genes
gene2go_selection     <- gene2go[raw_selectionGenes$droso_gene]
gene2go_selectionSame <- gene2go[intersect(names(gene2go),
                                           PredictorGenes)]



# I want the pvalue and the number of SVM sig genes
interesting_go_term_metadata <- myTable[myTable$GO.ID %in%
                                          as.character(one.data$term_ID),]

# combine information
one.data$pvalue <- interesting_go_term_metadata$pvalue[match(one.data$term_ID,
                                      interesting_go_term_metadata$GO.ID)]

# add number of SVM genes related to given GO terms 
one.data$Significant <- 
  interesting_go_term_metadata$Significant[match(one.data$term_ID,
          interesting_go_term_metadata$GO.ID)]



# --------------------------------------------------------------------------
# Names of the axes, sizes of the numbers and letters, names of the columns,
# etc. can be changed below

coul <- c("#7A0177", "#D12790", "#F883AB")
#rev_coul <- c("#FFF7F3", "#FCCBC7","#F883AB","#D12790","#7A0177")

# top 5 five Terms with high uniqueness
# with regard to the whole of Drosophila (0.78 to 1)
summary(one.data$uniqueness)
sort(one.data$uniqueness)
one.data$description[one.data$uniqueness == 1]

# I chose the most relevent to our study system
high_uniqueness_terms <- c("reproduction",
                           "immune system process",
                           "behavior" ,
                           "metabolic process", 
                           "response to stimulus" )

# top 5 Terms with low dispensability (0 to 0.6)
# high value == strong redundancy with respect to the chosen representative
# so low value == quite unique
# this takes in account pvalue (that we did not include)
summary(one.data$dispensability)
sort(one.data$dispensability)
one.data$description[one.data$dispensability == 0]

# I chose the most relevent to our study system
# few are similar to the high uniqueness
low_dispensability_terms <- c("developmental process" , 
                           "single fertilization" )


# make the list of genes that we want highlighted
# they are significant SVM GO terms, or strong in the overlap SVM-DEG-WCGNA
noticeable_terms <- c("regulation of developmental process",
                  "negative regulation of chromatin organization",
                  "regulation of telomere maintenance",
                  "reproductive behavior",
                  "negative regulation of insulin receptor signaling pathway",
                  "histone H3-K23 acetylation",
                  "regulation of RNA splicing",
                  "olfactory behavior",
                  "chemosensory behavior",
                  "immune system process", 
                  high_uniqueness_terms, low_dispensability_terms)

# subset to those terms
ex <- one.data %>% filter(description %in% noticeable_terms)

# create the range for the x and y axis
one.x_range = max(one.data$plot_X) - min(one.data$plot_X);
one.y_range = max(one.data$plot_Y) - min(one.data$plot_Y);

# colour gradient, from dark green to light green
greens <- c("#e5f5e0", "#a1d99b", "#31a354")

# colours == uniqueness
# 0/light = term is not unique amongst the list of terms (sort of redundant)
# 1/dark = strong semantic uniqueness with respect to other terms 

ggplot(data = one.data) + 
  geom_point(aes(plot_X, plot_Y,
                            colour = uniqueness,
                            size = Significant), 
                       alpha = I(0.6) ) + 
  scale_colour_gradientn(colours = greens,
                           limits = c(0, 1) )+ 
  geom_point(aes(plot_X, plot_Y, size = Significant),
                       shape = 21, fill = "transparent",
                       colour = I (alpha ("black", 0.6) )) + 
  scale_size("Number of associated predictor genes",
             range = c(0,15)) +
  theme_bw() + 
  geom_text( data = ex,
             aes(plot_X, plot_Y,
                 label = description),
             colour = I(alpha("black", 0.85)), size = 3 ) +
  labs (y = "semantic space x", x = "semantic space y") + 
  theme(legend.key = element_blank())  + 
  xlim(min(one.data$plot_X)-one.x_range/10,max(one.data$plot_X)+one.x_range/10) +
  ylim(min(one.data$plot_Y)-one.y_range/10,max(one.data$plot_Y)+one.y_range/10);



# save the figure for manuscript
ggsave("2021-12-15-revigo-species-normalised-plot.pdf")

# caption
# REVIGO Semantic relationships of GO Terms associated with the SVM predictor genes.
# Darker dots are GO Terms that are semantically outlier amongst the GO Terms list.
# Larger dots are GO Terms associated with the highest number of predictor genes.
# Noticeable terms are labelled.


# save a table for supplementary info
interesting_go_term_metadata$uniqueness <-
  one.data$uniqueness[match(interesting_go_term_metadata$GO.ID,
     one.data$term_ID)]

interesting_go_term_metadata$dispensability <- 
  one.data$dispensability[match(interesting_go_term_metadata$GO.ID,
     one.data$term_ID)]

interesting_go_term_metadata$frequency <- 
  one.data$frequency[match(interesting_go_term_metadata$GO.ID,
     one.data$term_ID)]

write.csv(interesting_go_term_metadata,
            file = "go_term_metadata_127_predictor_genes.csv",
            quote = FALSE,
            row.names = FALSE)




```
