---
title: "TopGo analysis from WGNCA GO Slim Terms (GO SLIMMER)"
author: "Emeline Favreau"
date: "22/03/2021"
output: html_document
---
Copyright 2021 Emeline Favreau, University College London.


###### Objective of analysis: Among the 3 wasp and 3 bee species, are there common pattern of GO Slim Term enrichment?

We obtained GO terms that are significantly enriched in our dataset subsets: genes that are in WGCNA modules significantly correlated with reproductive status (reproductives and non-reproductives) in _Ceratina australensis_, _C. calcarata_, _Megalopta genalis_, _Polistes canadensis_, _P. dominula_ and _Liostenogaster flavolineata_.


###### Analysis steps:
- Obtaining data
- Aim 1: Biological processes enrichment
- Aim 2: Molecular function enrichment
- Aim 3: Cellular component enrichment




```{r load all the libraries, eval = TRUE, echo = FALSE, include = FALSE}
# get libraries
basic_libraries <- c("ggplot2",
                     "tidyverse",
                     "readr")

for (lib in basic_libraries) {
        if (require(package = lib, character.only = TRUE)) {
                print("Successful")
        } else {
                print("Installing")
                install.packages(lib)
                library(lib, character.only = TRUE )
        }
}
```

```{r list common groups}


# the groups that we are testing
all_species <- c("Polistes_canadensis",
          "Polistes_dominula",
          "Liostenogaster_flavolineata",
          "Ceratina_australensis",
          "Ceratina_calcarata" ,
          "Megalopta_genalis")

wasp <- c("Polistes_canadensis",
          "Polistes_dominula",
          "Liostenogaster_flavolineata")

bee <- c("Ceratina_australensis",
          "Ceratina_calcarata" ,
          "Megalopta_genalis")

```

##### Aim 1: Biological processes enrichment in all significant WGCNA


```{r import data BP all sig WGCNA, eval = TRUE, echo = FALSE, include = FALSE}
# GO terms enrichment result tables
# file obtained by TopGO, containing data description
# GO.ID	Term	Annotated	Significant	Expected	pvalue	species	dataSubset	goCategory
# these are Biological processes for DEG upregulated in WGCNA
Ceratina_australensis_BP <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Ceratina_australensis_BP",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Ceratina_calcarata_BP <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Ceratina_calcarata_BP",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Megalopta_genalis_BP <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Megalopta_genalis_BP",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Polistes_dominula_BP <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Polistes_dominula_BP",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Polistes_canadensis_BP <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Polistes_canadensis_BP",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Liostenogaster_flavolineata_BP <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Liostenogaster_flavolineata_BP",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

```

```{r make table BP , eval = TRUE, echo = FALSE, include = TRUE}
# subset for the important data 
australensis_table_BP <- Ceratina_australensis_BP %>% 
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

dominula_table_BP <- Polistes_dominula_BP %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

genalis_table_BP <- Megalopta_genalis_BP %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

canadensis_table_BP <- Polistes_canadensis_BP %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

calcarata_table_BP <- Ceratina_calcarata_BP %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

flavolineata_table_BP <- Liostenogaster_flavolineata_BP %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

# result table: number of significant GO Terms for each species
result_BP_df  <-  as.data.frame(rbind(c("Ceratina_australensis",
                                        nrow(australensis_table_BP)),
                                      c("Ceratina_calcarata",
                                        nrow(calcarata_table_BP)),
                                      c("Megalopta_genalis",
                                        nrow(genalis_table_BP)),
                                      c("Polistes_dominula",
                                        nrow(dominula_table_BP)),
                                      c("Polistes_canadensis",
                                        nrow(canadensis_table_BP)),
                                      c("Liostenogaster_flavolineata",
                                        nrow(flavolineata_table_BP))),
    stringsAsFactors = FALSE)

colnames(result_BP_df) <- c("species", "Sig_GO_Term_in_BP")

result_BP_df

# obtain vector of all GO
GO.ID_BP <- unique(c(australensis_table_BP$GO.ID,
                     dominula_table_BP$GO.ID,
                     genalis_table_BP$GO.ID,
                     canadensis_table_BP$GO.ID,
                     calcarata_table_BP$GO.ID,
                     flavolineata_table_BP$GO.ID))


# make a new table
# columns: GOID, Terms, species
stacked_result_BP <- rbind(australensis_table_BP,
                  dominula_table_BP,
                  genalis_table_BP,
                  canadensis_table_BP,
                  calcarata_table_BP,
                  flavolineata_table_BP)

# obtain frequencies of GO Terms for all aspecies
test <- stacked_result_BP

# dataframe
# GOID | Species 1 | Species 2 | Species 3 | 
wide_df <- as.data.frame(matrix(NA, nrow = length(unique(test$GO.ID)),
                                ncol = 7))
# name the columns
colnames(wide_df) <- c("GO.ID", all_species)

# make a vector with all GO terms
go_vec <- unique(test$GO.ID)

# assign thios go terms to the column
wide_df$GO.ID <- go_vec

# set all species column count to 0
wide_df$Polistes_canadensis         <- 0
wide_df$Polistes_dominula           <- 0
wide_df$Liostenogaster_flavolineata <- 0
wide_df$Ceratina_australensis       <- 0
wide_df$Ceratina_calcarata          <- 0
wide_df$Megalopta_genalis           <- 0

for(i in go_vec){
  
  # subset data for a given GO Term ID
  this_subset <- test %>% filter(GO.ID == i)
  
  # assign 1 if present in this species
  if("Ceratina_australensis" %in% this_subset$species){
    wide_df$Ceratina_australensis[wide_df$GO.ID == i] <- 1
  }
  
  if("Polistes_canadensis" %in% this_subset$species){
    wide_df$Polistes_canadensis[wide_df$GO.ID == i] <- 1
  }
  
  if("Polistes_dominula" %in% this_subset$species){
    wide_df$Polistes_dominula[wide_df$GO.ID == i] <- 1
  }
  
  if("Liostenogaster_flavolineata" %in% this_subset$species){
    wide_df$Liostenogaster_flavolineata[wide_df$GO.ID == i] <- 1
  }
  
  if("Ceratina_calcarata" %in% this_subset$species){
    wide_df$Ceratina_calcarata[wide_df$GO.ID == i] <- 1
  }
  
  if("Megalopta_genalis" %in% this_subset$species){
    wide_df$Megalopta_genalis[wide_df$GO.ID == i] <- 1
  }
}


# add a column with count of species that have that GO term  
wide_df$species_count <- wide_df %>%
  select(all_of(all_species)) %>%
  rowSums()

# add a column with Term
wide_df$GOTerm <- test$Term[match(wide_df$GO.ID, test$GO.ID)]

# add a column for BP
wide_df$GOCategory <- "BP"

# save for supplementary info
write.table(x         = wide_df,
            file      = "resultOnScratch/WGCNA_BP_GOSlimTerms.csv",
            quote     = FALSE,
            row.names = FALSE,
            sep       = ",")
```

Some overlap between species in GO Slim Terms.

```{r exploration of BP results}
## exploration of BP results
# Some overlap between species in GO Slim Terms.
## exploration of MF results
# there are 8 cases with 2 species that have common GO Terms
# summary(wide_df$species_count)
wide_df %>% filter(species_count == 2)

# Pdom and Mgen share 7 GO Slim Terms 
wide_df %>% filter(species_count == 2) %>% filter(Polistes_dominula == 1) %>% 
  filter(Megalopta_genalis == 1) %>% select(GO.ID, GOTerm)

# GO.ID                                       GOTerm
# 1 GO:0002181                      cytoplasmic translation
# 2 GO:0006412                                  translation
# 3 GO:0006518                    peptide metabolic process
# 4 GO:0043043                 peptide biosynthetic process
# 5 GO:0043603             cellular amide metabolic process
# 6 GO:0043604                   amide biosynthetic process
# 7 GO:1901566 organonitrogen compound biosynthetic process

# Pdom and Mgen share 1 GO Slim Term
wide_df %>% filter(species_count == 2) %>% filter(Polistes_dominula == 1) %>% 
  filter(Liostenogaster_flavolineata == 1) %>% select(GO.ID, GOTerm)
# GO:0006091 generation of precursor metabolites and energy

# list of 8 GO ID that are important for 2 species
common_BP_GO_vec <- as.vector(wide_df %>% filter(species_count == 2) %>%
   select(GO.ID))


test <- wide_df %>% filter(species_count == 2) %>%
   select(GO.ID)

# check description (expectation: sensory mechanisms)
# but we see mainly synaptic and cellular processes
common_BP_GOTerms_df <- stacked_result_BP %>% 
  filter(GO.ID %in% common_BP_GO_vec$GO.ID) 

# save this list
write.table(x        = common_BP_GOTerms_df,
            file      = "resultOnScratch/WGCNA_common_BP_GOSlimTerms.csv",
            quote     = FALSE,
            row.names = FALSE,
            sep       = ",")


```


##### Aim 2: Molecular Functions enrichment in WGCNA



```{r import data MF all WGCNA, eval = TRUE, echo = FALSE, include = FALSE}
# GO terms enrichment result tables
# file obtained by TopGO, containing data description
# GO.ID	Term	Annotated	Significant	Expected	pvalue	species	dataSubset	goCategory
# these are Biological processes for WGCNA
Ceratina_australensis_MF <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Ceratina_australensis_MF",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Ceratina_calcarata_MF <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Ceratina_calcarata_MF",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Megalopta_genalis_MF <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Megalopta_genalis_MF",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Polistes_dominula_MF <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Polistes_dominula_MF",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Polistes_canadensis_MF <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Polistes_canadensis_MF",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Liostenogaster_flavolineata_MF <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Liostenogaster_flavolineata_MF",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

```

```{r make table MF , eval = TRUE, echo = FALSE, include = TRUE}
# subset for the important data 
australensis_table_MF <- Ceratina_australensis_MF %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

dominula_table_MF <- Polistes_dominula_MF %>% 
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

genalis_table_MF <- Megalopta_genalis_MF %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

canadensis_table_MF <- Polistes_canadensis_MF %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

calcarata_table_MF <- Ceratina_calcarata_MF %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

flavolineata_table_MF <- Liostenogaster_flavolineata_MF %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

# result table: number of significant GO Terms for each species
result_MF_df  <-  as.data.frame(rbind(c("Ceratina_australensis",
                                        nrow(australensis_table_MF)),
                                      c("Ceratina_calcarata",
                                        nrow(calcarata_table_MF)),
                                      c("Megalopta_genalis",
                                        nrow(genalis_table_MF)),
                                      c("Polistes_dominula",
                                        nrow(dominula_table_MF)),
                                      c("Polistes_canadensis",
                                        nrow(canadensis_table_MF)),
                                      c("Liostenogaster_flavolineata",
                                        nrow(flavolineata_table_MF))),
    stringsAsFactors = FALSE)

colnames(result_MF_df) <- c("species", "Sig_GO_Term_in_MF")

result_MF_df

# obtain vector of all GO
GO.ID_MF <- unique(c(australensis_table_MF$GO.ID,
                     dominula_table_MF$GO.ID,
                     genalis_table_MF$GO.ID,
                     canadensis_table_MF$GO.ID,
                     calcarata_table_MF$GO.ID,
                     flavolineata_table_MF$GO.ID))


# make a new table
# columns: GOID, Terms, species
stacked_result_MF <- rbind(australensis_table_MF,
                  dominula_table_MF,
                  genalis_table_MF,
                  canadensis_table_MF,
                  calcarata_table_MF,
                  flavolineata_table_MF)

# obtain frequencies of GO Terms for all aspecies
test <- stacked_result_MF

# dataframe
# GOID | Species 1 | Species 2 | Species 3 | 
wide_df <- as.data.frame(matrix(NA, nrow = length(unique(test$GO.ID)),
                                ncol = 7))
# name the columns
colnames(wide_df) <- c("GO.ID", all_species)

# make a vector with all GO terms
go_vec <- unique(test$GO.ID)

# assign thios go terms to the column
wide_df$GO.ID <- go_vec

# set all species column count to 0
wide_df$Polistes_canadensis         <- 0
wide_df$Polistes_dominula           <- 0
wide_df$Liostenogaster_flavolineata <- 0
wide_df$Ceratina_australensis       <- 0
wide_df$Ceratina_calcarata          <- 0
wide_df$Megalopta_genalis           <- 0

for(i in go_vec){
  
  this_subset <- test %>% filter(GO.ID == i)
  
  if("Ceratina_australensis" %in% this_subset$species){
    wide_df$Ceratina_australensis[wide_df$GO.ID == i] <- 1
  }
  
  if("Polistes_canadensis" %in% this_subset$species){
    wide_df$Polistes_canadensis[wide_df$GO.ID == i] <- 1
  }
  
  if("Polistes_dominula" %in% this_subset$species){
    wide_df$Polistes_dominula[wide_df$GO.ID == i] <- 1
  }
  
  if("Liostenogaster_flavolineata" %in% this_subset$species){
    wide_df$Liostenogaster_flavolineata[wide_df$GO.ID == i] <- 1
  }
  
  if("Ceratina_calcarata" %in%this_subset$species){
    wide_df$Ceratina_calcarata[wide_df$GO.ID == i] <- 1
  }
  
  if("Megalopta_genalis" %in%this_subset$species){
    wide_df$Megalopta_genalis[wide_df$GO.ID == i] <- 1
  }
}


# add a column with count of species that have that GO term  
wide_df$species_count <- wide_df %>% select(all_of(all_species)) %>% rowSums()

# add a column with Term
wide_df$GOTerm <- test$Term[match(wide_df$GO.ID, test$GO.ID)]

# add a column for MF
wide_df$GOCategory <- "MF"

# save for supplementary info
write.table(x         = wide_df,
            file      = "resultOnScratch/WGCNA_MF_GOSlimTerms.csv",
            quote     = FALSE,
            row.names = FALSE,
            sep       = ",")
```

.


```{r exploration of MF results}
## exploration of MF results
# there are 7 cases with 2 species that have common GO Terms
# summary(wide_df$species_count)
wide_df %>% filter(species_count == 2)

# 5 between Pdom and Mgen
# GO:0003735 structural constituent of ribosome
# 2 GO:0005198       structural molecule activity
# 3 GO:0016491            oxidoreductase activity
# 4 GO:0005215               transporter activity
# 5 GO:0022857 transmembrane transporter activity
wide_df %>% filter(species_count == 2) %>% 
  filter(Polistes_dominula ==1) %>% 
  filter(Megalopta_genalis == 1) %>%  select(GO.ID, GOTerm)

# 2 between Liostenogaster_flavolineata Ceratina_australensis
# GO:0042302            structural constituent of cuticle
# 2 GO:0016798 hydrolase activity, acting on glycosyl bonds
wide_df %>% filter(species_count == 2) %>% 
  filter(Liostenogaster_flavolineata ==1) %>% 
  filter(Ceratina_australensis == 1) %>%  select(GO.ID, GOTerm)

# list of 7 GO ID that are important for 2 or 3  species
common_MF_GO_vec <- unique(c("GO:0003735", "GO:0005198", "GO:0016491",
                             "GO:0005215", "GO:0022857", "GO:0042302",
                             "GO:0016798"))


test <- wide_df %>% 
  filter(GO.ID %in% common_MF_GO_vec) 

# check description (expectation: sensory mechanisms)
# but we see mainly synaptic and cellular processes
common_MF_GOTerms_df <- stacked_result_MF %>% 
  filter(GO.ID %in% common_MF_GO_vec) 

# save this list
write.table(x    = common_MF_GOTerms_df,
            file = "resultOnScratch/WGCNA_common_MF_GOSlimTerms.csv",
            quote = FALSE,
            row.names = FALSE,
            sep = ",")
```
7 GO Slim Terms of Molecular Function are shared by 2 species (wasp and bee).



##### Aim 3: Cellular component enrichment in WGCNA



```{r import data CC WGCNA, eval = TRUE, echo = FALSE, include = FALSE}
# GO terms enrichment result tables
# file obtained by TopGO, containing data description
# GO.ID	Term	Annotated	Significant	Expected	pvalue	species	dataSubset	goCategory
# these are Biological processes for WGCNA
Ceratina_australensis_CC <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Ceratina_australensis_CC",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Ceratina_calcarata_CC <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Ceratina_calcarata_CC",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Megalopta_genalis_CC <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Megalopta_genalis_CC",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Polistes_dominula_CC <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Polistes_dominula_CC",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Polistes_canadensis_CC <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Polistes_canadensis_CC",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

Liostenogaster_flavolineata_CC <- read_delim("resultOnScratch/topgo_result_WGCNA_slimTerms_Liostenogaster_flavolineata_CC",
                                    "\t", escape_double = FALSE, trim_ws = TRUE)

```

```{r make table CC , eval = TRUE, echo = FALSE, include = TRUE}
# subset for the important data 
australensis_table_CC <- Ceratina_australensis_CC %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

dominula_table_CC <- Polistes_dominula_CC %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

genalis_table_CC <- Megalopta_genalis_CC %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

canadensis_table_CC <- Polistes_canadensis_CC %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

calcarata_table_CC <- Ceratina_calcarata_CC %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

flavolineata_table_CC <- Liostenogaster_flavolineata_CC %>%
  filter(pvalue < 0.05) %>%
  select(GO.ID, species, Term)

# result table: number of significant GO Terms for each species
result_CC_df  <-  as.data.frame(rbind(c("Ceratina_australensis",
                                        nrow(australensis_table_CC)),
                                      c("Ceratina_calcarata",
                                        nrow(calcarata_table_CC)),
                                      c("Megalopta_genalis",
                                        nrow(genalis_table_CC)),
                                      c("Polistes_dominula",
                                        nrow(dominula_table_CC)),
                                      c("Polistes_canadensis",
                                        nrow(canadensis_table_CC)),
                                      c("Liostenogaster_flavolineata",
                                        nrow(flavolineata_table_CC))),
    stringsAsFactors = FALSE)

colnames(result_CC_df) <- c("species", "Sig_GO_Term_in_CC")

result_CC_df

# obtain vector of all GO
GO.ID_CC <- unique(c(australensis_table_CC$GO.ID,
                     dominula_table_CC$GO.ID,
                     genalis_table_CC$GO.ID,
                     canadensis_table_CC$GO.ID,
                     calcarata_table_CC$GO.ID,
                     flavolineata_table_CC$GO.ID))


# make a new table
# columns: GOID, Terms, species
stacked_result_CC <- rbind(australensis_table_CC,
                  dominula_table_CC,
                  genalis_table_CC,
                  canadensis_table_CC,
                  calcarata_table_CC,
                  flavolineata_table_CC)

# obtain frequencies of GO Terms for all aspecies
test <- stacked_result_CC

# dataframe
# GOID | Species 1 | Species 2 | Species 3 | 
wide_df <- as.data.frame(matrix(NA, nrow = length(unique(test$GO.ID)),
                                ncol = 7))
# name the columns
colnames(wide_df) <- c("GO.ID", all_species)

# make a vector with all GO terms
go_vec <- unique(test$GO.ID)

# assign thios go terms to the column
wide_df$GO.ID <- go_vec

# set all species column count to 0
wide_df$Polistes_canadensis         <- 0
wide_df$Polistes_dominula           <- 0
wide_df$Liostenogaster_flavolineata <- 0
wide_df$Ceratina_australensis       <- 0
wide_df$Ceratina_calcarata          <- 0
wide_df$Megalopta_genalis           <- 0

for(i in go_vec){
  
  this_subset <- test %>% filter(GO.ID == i)
  
  if("Ceratina_australensis" %in% this_subset$species){
    wide_df$Ceratina_australensis[wide_df$GO.ID == i] <- 1
  }
  
  if("Polistes_canadensis" %in% this_subset$species){
    wide_df$Polistes_canadensis[wide_df$GO.ID == i] <- 1
  }
  
  if("Polistes_dominula" %in% this_subset$species){
    wide_df$Polistes_dominula[wide_df$GO.ID == i] <- 1
  }
  
  if("Liostenogaster_flavolineata" %in% this_subset$species){
    wide_df$Liostenogaster_flavolineata[wide_df$GO.ID == i] <- 1
  }
  
  if("Ceratina_calcarata" %in%this_subset$species){
    wide_df$Ceratina_calcarata[wide_df$GO.ID == i] <- 1
  }
  
  if("Megalopta_genalis" %in%this_subset$species){
    wide_df$Megalopta_genalis[wide_df$GO.ID == i] <- 1
  }
}


# add a column with count of species that have that GO term  
wide_df$species_count <- wide_df %>% 
  select(all_of(all_species)) %>% rowSums()


# add a column with Term
wide_df$GOTerm <- test$Term[match(wide_df$GO.ID, test$GO.ID)]

# add a column for CC
wide_df$GOCategory <- "CC"

# save for supplementary info
write.table(x         = wide_df,
            file      = "resultOnScratch/WGCNA_CC_GOSlimTerms.csv",
            quote     = FALSE,
            row.names = FALSE,
            sep       = ",")
```




```{r exploration of CC results}
## exploration of CC results
# there is 1 GO Slim Term shared between two species
# summary(wide_df$species_count)
# save GO:0045202 synapse between Pdom and Mgen
wide_df %>% filter(species_count == 2) 




```
1 GO Terms of Cellular Component  are shared by 2 species (bee and wasp).





**Conclusion**



```{r record versions of session, eval = TRUE, echo = FALSE, include = FALSE}
# record versions of R and packages here
sessionInfo()
# R version 3.6.3 (2020-02-29)
# Platform: x86_64-apple-darwin15.6.0 (64-bit)
# Running under: macOS Catalina 10.15.4
# 
# Matrix products: default
# BLAS:   /System/Library/Frameworks/Accelerate.framework/Versions/A/Frameworks/vecLib.framework/Versions/A/libBLAS.dylib
# LAPACK: /Library/Frameworks/R.framework/Versions/3.6/Resources/lib/libRlapack.dylib
# 
# locale:
# [1] en_GB.UTF-8/en_GB.UTF-8/en_GB.UTF-8/C/en_GB.UTF-8/en_GB.UTF-8
# 
# attached base packages:
# [1] stats     graphics  grDevices utils     datasets  methods   base     
# 
# other attached packages:
# [1] forcats_0.5.0   stringr_1.4.0   dplyr_0.8.5     purrr_0.3.4     readr_1.3.1    
# [6] tidyr_1.0.3     tibble_3.0.1    tidyverse_1.3.0 ggplot2_3.3.0  
# loaded via a namespace (and not attached):
#  [1] Rcpp_1.0.4.6     cellranger_1.1.0 pillar_1.4.4     compiler_3.6.3   dbplyr_1.4.3    
#  [6] tools_3.6.3      lubridate_1.7.8  jsonlite_1.6.1   lifecycle_0.2.0  gtable_0.3.0    
# [11] nlme_3.1-147     lattice_0.20-41  pkgconfig_2.0.3  rlang_0.4.6      reprex_0.3.0    
# [16] cli_2.0.2        DBI_1.1.0        rstudioapi_0.11  yaml_2.2.1       haven_2.2.0     
# [21] xfun_0.13        xml2_1.3.2       withr_2.2.0      httr_1.4.1       knitr_1.28      
# [26] fs_1.4.1         generics_0.0.2   vctrs_0.3.0      hms_0.5.3        grid_3.6.3      
# [31] tidyselect_1.1.0 glue_1.4.1       R6_2.4.1         fansi_0.4.1      readxl_1.3.1    
# [36] modelr_0.1.7     magrittr_1.5     scales_1.1.1     backports_1.1.7  ellipsis_0.3.0  
# [41] rvest_0.3.5      assertthat_0.2.1 colorspace_1.4-1 stringi_1.4.6    munsell_0.5.0   
# [46] broom_0.5.6      crayon_1.3.4 
```
