---
title: "GO Terms in WGCNA consensus"
author: "Emeline Favreau"
date: "2021-10-25"
output: html_document
---

Copyright 2021 Emeline Favreau, University College London.

TopGO results from orthogroups from WGCNA consensus method, in which species' read counts were pooled together: either all six species, or all bees (three species) or all wasps (three species). We extended the analysis by allowing two sizes of WGCNA modules: the standard (n = 30 genes) and a lower threshold (n = 10 genes).

Here we test for significance of GO term enrichment.

---
# Objective of analysis

## Analysis steps:
- Aim 1: Significant GO Terms associated with consensus WGCNA module size 30, all species (BP, CC, MF)
- Aim 2: Significant GO Terms associated with consensus WGCNA module size 10, all species (BP, CC, MF)
- Aim 3: Significant GO Terms associated with consensus WGCNA module size 30, wasps only (BP, CC, MF)
- Aim 4: Significant GO Terms associated with consensus WGCNA module size 10, wasps only (BP, CC, MF)
- Aim 5: Significant GO Terms associated with consensus WGCNA module size 30, bees only (BP, CC, MF)
- Aim 6: Significant GO Terms associated with consensus WGCNA module size 10, beess only (BP, CC, MF)


```{r load all the libraries, eval = TRUE, echo = FALSE, include = TRUE}
# get libraries
basic_libraries <- c("ggplot2",
                     "tidyverse",
                     "dplyr")

for (lib in basic_libraries) {
        if (require(package = lib, character.only = TRUE)) {
                print("Successful")
        } else {
                print("Installing")
                install.packages(lib)
                library(lib, character.only = TRUE )
        }
}
```

## Aim 1: Consensus with all six species (module size = 30 genes)

```{r 30 all BP, eval = TRUE, echo = FALSE, include = TRUE}
# six species, BP, module size 30
thirty_all_BP <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_30/all/topgo_result_BP")

# change class
thirty_all_BP$GO.ID <- as.character(thirty_all_BP$GO.ID)
thirty_all_BP$Term <- as.character(thirty_all_BP$Term)

# adjust for multiple comparison
thirty_all_BP$padj <- p.adjust(p = thirty_all_BP$pvalue, method = "BH")
summary(thirty_all_BP$padj)

```

```{r 30 all CC, eval = TRUE, echo = FALSE, include = TRUE}
# six species, CC, module size 30
thirty_all_CC <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_30/all/topgo_result_CC")

# change class
thirty_all_CC$GO.ID <- as.character(thirty_all_CC$GO.ID)
thirty_all_CC$Term <- as.character(thirty_all_CC$Term)

# adjust for multiple comparison
thirty_all_CC$padj <- p.adjust(p = thirty_all_CC$pvalue, method = "BH")
summary(thirty_all_CC$padj)
thirty_all_CC[thirty_all_CC$padj <= 0.05, ]

# add a column for module size
thirty_all_CC$module_size <- 30

# save significant results to a summary table
significant_results <- thirty_all_CC[thirty_all_CC$padj <= 0.05, ]
```


```{r 30 all MF, eval = TRUE, echo = FALSE, include = TRUE}
# six species, MF, module size 30
thirty_all_MF <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_30/all/topgo_result_MF")

# change class
thirty_all_MF$GO.ID <- as.character(thirty_all_MF$GO.ID)
thirty_all_MF$Term <- as.character(thirty_all_MF$Term)

# adjust for multiple comparison
thirty_all_MF$padj <- p.adjust(p = thirty_all_MF$pvalue, method = "BH")
summary(thirty_all_MF$padj)
thirty_all_MF[thirty_all_MF$padj <= 0.05, ]

# add a column for module size
thirty_all_MF$module_size <- 30

# save significant results to a summary table
significant_results <- rbind(significant_results,
                             thirty_all_MF[thirty_all_MF$padj <= 0.05, ])

```

In the consensus of all six species, there are no significant BP terms that are enriched. There are however some significant CC and MF enriched terms ("cellular compenent", very vague!)


## Aim 2: Consensus with all six species (module size = 10 genes)

```{r 10 all BP, eval = TRUE, echo = FALSE, include = TRUE}
# six species, BP, module size 30
ten_all_BP <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_10/all/topgo_result_BP")

# change class
ten_all_BP$GO.ID <- as.character(ten_all_BP$GO.ID)
ten_all_BP$Term <- as.character(ten_all_BP$Term)

# adjust for multiple comparison
ten_all_BP$padj <- p.adjust(p = ten_all_BP$pvalue, method = "BH")
summary(ten_all_BP$padj)
ten_all_BP[ten_all_BP$padj <= 0.05, ]

# add a column for module size
ten_all_BP$module_size <- 10

# save significant results to a summary table
significant_results <- rbind(significant_results,
                             ten_all_BP[ten_all_BP$padj <= 0.05, ])

```

```{r 10 all CC, eval = TRUE, echo = FALSE, include = TRUE}
# six species, CC, module size 30
ten_all_CC <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_10/all/topgo_result_CC")

# change class
ten_all_CC$GO.ID <- as.character(ten_all_CC$GO.ID)
ten_all_CC$Term <- as.character(ten_all_CC$Term)

# adjust for multiple comparison
ten_all_CC$padj <- p.adjust(p = ten_all_CC$pvalue, method = "BH")
summary(ten_all_CC$padj)
ten_all_CC[ten_all_CC$padj <= 0.05, ]

# add a column for module size
ten_all_CC$module_size <- 10

# save significant results to a summary table
significant_results <- rbind(significant_results,
                             ten_all_CC[ten_all_BP$padj <= 0.05, ])

```

```{r 10 all MF, eval = TRUE, echo = FALSE, include = TRUE}
# six species, MF, module size 30
ten_all_MF <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_10/all/topgo_result_MF")

# change class
ten_all_MF$GO.ID <- as.character(ten_all_MF$GO.ID)
ten_all_MF$Term <- as.character(ten_all_MF$Term)

# adjust for multiple comparison
ten_all_MF$padj <- p.adjust(p = ten_all_MF$pvalue, method = "BH")
summary(ten_all_MF$padj)
ten_all_MF[ten_all_MF$padj <= 0.05, ]

# add a column for module size
ten_all_MF$module_size <- 10

# save significant results to a summary table
significant_results <- rbind(significant_results,
                             ten_all_MF[ten_all_MF$padj <= 0.05, ])

```

In the consensus of all six species with a module size of 10 genes, there are nine significant BP terms that are enriched (metabolic, cellular component, regulation of chromatin assembly). There are also some significant CC and MF enriched terms ("cellular compenent", very vague!)

## Aim 3: Consensus with all wasp species (module size = 30 genes)

```{r 30 wasps BP, eval = TRUE, echo = FALSE, include = TRUE}
# six species, BP, module size 30
thirty_wasps_BP <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_30/wasps/topgo_result_BP")
thirty_wasps_BP$species <- "all wasps"
# change class
thirty_wasps_BP$GO.ID <- as.character(thirty_wasps_BP$GO.ID)
thirty_wasps_BP$Term <- as.character(thirty_wasps_BP$Term)

# adjust for multiple comparison
thirty_wasps_BP$padj <- p.adjust(p = thirty_wasps_BP$pvalue, method = "BH")
summary(thirty_wasps_BP$padj)

```

```{r 30 wasps CC, eval = TRUE, echo = FALSE, include = TRUE}
# six species, CC, module size 30
thirty_wasps_CC <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_30/wasps/topgo_result_CC")
thirty_wasps_CC$species <- "all wasps"
# change class
thirty_wasps_CC$GO.ID <- as.character(thirty_wasps_CC$GO.ID)
thirty_wasps_CC$Term <- as.character(thirty_wasps_CC$Term)

# adjust for multiple comparison
thirty_wasps_CC$padj <- p.adjust(p = thirty_wasps_CC$pvalue, method = "BH")
summary(thirty_wasps_CC$padj)
#thirty_wasps_CC[thirty_wasps_CC$padj <= 0.05, ]

```
```{r 30 wasps MF, eval = TRUE, echo = FALSE, include = TRUE}
# six species, MF, module size 30
thirty_wasps_MF <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_30/wasps/topgo_result_MF")
thirty_wasps_MF$species <- "all wasps"
# change class
thirty_wasps_MF$GO.ID <- as.character(thirty_wasps_MF$GO.ID)
thirty_wasps_MF$Term <- as.character(thirty_wasps_MF$Term)

# adjust for multiple comparison
thirty_wasps_MF$padj <- p.adjust(p = thirty_wasps_MF$pvalue, method = "BH")
summary(thirty_wasps_MF$padj)
#thirty_wasps_CC[thirty_wasps_MF$padj <= 0.05, ]

```

In the consensus of all wasps species, there are no significant GO terms that are enriched.


## Aim 4: Consensus with all wasps species (module size = 10 genes)

```{r 10 wasps BP, eval = TRUE, echo = FALSE, include = TRUE}
# six species, BP, module size 30
ten_wasps_BP <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_10/wasps/topgo_result_BP")
ten_wasps_BP$species <- "all wasps"
# change class
ten_wasps_BP$GO.ID <- as.character(ten_wasps_BP$GO.ID)
ten_wasps_BP$Term <- as.character(ten_wasps_BP$Term)

# adjust for multiple comparison
ten_wasps_BP$padj <- p.adjust(p = ten_wasps_BP$pvalue, method = "BH")
summary(ten_wasps_BP$padj)
#ten_wasps_BP[ten_wasps_BP$padj <= 0.05, ]

```

```{r 10 wasps CC, eval = TRUE, echo = FALSE, include = TRUE}
# six species, CC, module size 30
ten_wasps_CC <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_10/wasps/topgo_result_CC")
ten_wasps_CC$species <- "all wasps"
# change class
ten_wasps_CC$GO.ID <- as.character(ten_wasps_CC$GO.ID)
ten_wasps_CC$Term <- as.character(ten_wasps_CC$Term)

# adjust for multiple comparison
ten_wasps_CC$padj <- p.adjust(p = ten_wasps_CC$pvalue, method = "BH")
summary(ten_wasps_CC$padj)
#ten_wasps_CC[ten_wasps_CC$padj <= 0.05, ]

```

```{r 10 wasps MF, eval = TRUE, echo = FALSE, include = TRUE}
# six species, MF, module size 30
ten_wasps_MF <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_10/wasps/topgo_result_MF")
ten_wasps_MF$species <- "all wasps"
# change class
ten_wasps_MF$GO.ID <- as.character(ten_wasps_MF$GO.ID)
ten_wasps_MF$Term <- as.character(ten_wasps_MF$Term)

# adjust for multiple comparison
ten_wasps_MF$padj <- p.adjust(p = ten_wasps_MF$pvalue, method = "BH")
summary(ten_wasps_MF$padj)
#ten_wasps_MF[ten_wasps_MF$padj <= 0.05, ]

```

In the consensus of all wasps species with a module size of 10 genes, there is no significant GO Terms that are enriched.


## Aim 5: Consensus with all bees species (module size = 30 genes)

```{r 30 bees BP, eval = TRUE, echo = FALSE, include = TRUE}
# six species, BP, module size 30
thirty_bees_BP <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_30/bees/topgo_result_BP")
thirty_bees_BP$species <- "all bees"
# change class
thirty_bees_BP$GO.ID <- as.character(thirty_bees_BP$GO.ID)
thirty_bees_BP$Term <- as.character(thirty_bees_BP$Term)

# adjust for multiple comparison
thirty_bees_BP$padj <- p.adjust(p = thirty_bees_BP$pvalue, method = "BH")
summary(thirty_bees_BP$padj)
thirty_bees_BP[thirty_bees_BP$padj <= 0.05, ]

# add a column for module size
thirty_bees_BP$module_size <- 30

# save significant results to a summary table
significant_results <- rbind(significant_results,
                             thirty_bees_BP[thirty_bees_BP$padj <= 0.05, ])
```

```{r 30 bees CC, eval = TRUE, echo = FALSE, include = TRUE}
# six species, CC, module size 30
thirty_bees_CC <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_30/bees/topgo_result_CC")
thirty_bees_CC$species <- "all bees"
# change class
thirty_bees_CC$GO.ID <- as.character(thirty_bees_CC$GO.ID)
thirty_bees_CC$Term <- as.character(thirty_bees_CC$Term)

# adjust for multiple comparison
thirty_bees_CC$padj <- p.adjust(p = thirty_bees_CC$pvalue, method = "BH")
summary(thirty_bees_CC$padj)
thirty_bees_CC[thirty_bees_CC$padj <= 0.05, ]

# add a column for module size
thirty_bees_CC$module_size <- 30

# save significant results to a summary table
significant_results <- rbind(significant_results,
                             thirty_bees_CC[thirty_bees_CC$padj <= 0.05, ])

```
```{r 30 bees MF, eval = TRUE, echo = FALSE, include = TRUE}
# six species, MF, module size 30
thirty_bees_MF <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_30/bees/topgo_result_MF")
thirty_bees_MF$species <- "all bees"
# change class
thirty_bees_MF$GO.ID <- as.character(thirty_bees_MF$GO.ID)
thirty_bees_MF$Term <- as.character(thirty_bees_MF$Term)

# adjust for multiple comparison
thirty_bees_MF$padj <- p.adjust(p = thirty_bees_MF$pvalue, method = "BH")
summary(thirty_bees_MF$padj)
thirty_bees_MF[thirty_bees_MF$padj <= 0.05, ]

# add a column for module size
thirty_bees_MF$module_size <- 30

# save significant results to a summary table
significant_results <- rbind(significant_results,
                             thirty_bees_MF[thirty_bees_MF$padj <= 0.05, ])

```

In the consensus of all bees species, there are many significant GO terms that are enriched: 49 BP terms (e.g. regulation, tissue and gland devlopment), 7 CC terms and 11 MF terms (mainly cellular component).


## Aim 6: Consensus with all bees species (module size = 10 genes)

```{r 10 bees BP, eval = TRUE, echo = FALSE, include = TRUE}
# six species, BP, module size 30
ten_bees_BP <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_10/bees/topgo_result_BP")
ten_bees_BP$species <- "all bees"
# change class
ten_bees_BP$GO.ID <- as.character(ten_bees_BP$GO.ID)
ten_bees_BP$Term <- as.character(ten_bees_BP$Term)

# adjust for multiple comparison
ten_bees_BP$padj <- p.adjust(p = ten_bees_BP$pvalue, method = "BH")
summary(ten_bees_BP$padj)
ten_bees_BP[ten_bees_BP$padj <= 0.05, ]

# add a column for module size
ten_bees_BP$module_size <- 10

# save significant results to a summary table
significant_results <- rbind(significant_results,
                             ten_bees_BP[ten_bees_BP$padj <= 0.05, ])

```

```{r 10 bees CC, eval = TRUE, echo = FALSE, include = TRUE}
# six species, CC, module size 30
ten_bees_CC <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_10/bees/topgo_result_CC")
ten_bees_CC$species <- "all bees"
# change class
ten_bees_CC$GO.ID <- as.character(ten_bees_CC$GO.ID)
ten_bees_CC$Term <- as.character(ten_bees_CC$Term)

# adjust for multiple comparison
ten_bees_CC$padj <- p.adjust(p = ten_bees_CC$pvalue, method = "BH")
summary(ten_bees_CC$padj)
ten_bees_CC[ten_bees_CC$padj <= 0.05, ]

# add a column for module size
ten_bees_CC$module_size <- 10

# save significant results to a summary table
significant_results <- rbind(significant_results,
                             ten_bees_CC[ten_bees_CC$padj <= 0.05, ])


```

```{r 10 bees MF, eval = TRUE, echo = FALSE, include = TRUE}
# six species, MF, module size 30
ten_bees_MF <- read.delim("~/working-dir-GOTIT/WGCNA/result/module_size_10/bees/topgo_result_MF")
ten_bees_MF$species <- "all bees"
# change class
ten_bees_MF$GO.ID <- as.character(ten_bees_MF$GO.ID)
ten_bees_MF$Term <- as.character(ten_bees_MF$Term)

# adjust for multiple comparison
ten_bees_MF$padj <- p.adjust(p = ten_bees_MF$pvalue, method = "BH")
summary(ten_bees_MF$padj)
ten_bees_MF[ten_bees_MF$padj <= 0.05, ]

# add a column for module size
ten_bees_MF$module_size <- 10

# save significant results to a summary table
significant_results <- rbind(significant_results,
                             ten_bees_MF[ten_bees_MF$padj <= 0.05, ])

# save result for supplementary info
write.table(x = significant_results,
            file = "../result/topgo_sig_go_terms",
            quote = FALSE,
            row.names = FALSE,
            sep = "\t")
# SVM GO term
svm_go_terms <- c("GO:0006090", "GO:0044331", "GO:0008362", "GO:0009112", "GO:0008052", "GO:0016339", "GO:0046661", "GO:0046034", "GO:0030239", "GO:0008045", "GO:0016999", "GO:0009144", "GO:0006270", "GO:0009126", "GO:0046496", "GO:0006790", "GO:0009141", "GO:0009123", "GO:0006732", "GO:0072522", "GO:0019693", "GO:0006091", "GO:0072521", "GO:0017144", "GO:0098662", "GO:0055086", "GO:0007268", "GO:0055114", "GO:0006412", "GO:0006811", "GO:0055085", "GO:0044281", "GO:0003008", "GO:0001895", "GO:0006026", "GO:0006099", "GO:0006101", "GO:0006826", "GO:0007310", "GO:0009416", "GO:0009581", "GO:0015918", "GO:0015985", "GO:0030488", "GO:0031497", "GO:0046154", "GO:0060180", "GO:0072350")

# find overlap between the two lists: "GO:0009126" "GO:0003008"
svm_go_terms[svm_go_terms %in% unique(significant_results$GO.ID)]
# purine nucleoside monophosphate metabolic process "GO:0009126"
# system process  "GO:0003008"

```

In the consensus of all bees species with a module size of 10 genes, there are many significant GO terms that are enriched: 44 BP terms (e.g. regulation, body growth, sensory), 12 CC terms and 12 MF terms (mainly cellular component).



## Conclusion

Our consensus analysis presents very few significant GO Terms for orthogroups that are in significant WGCNA modules and associated with being a reproductive or a non-reproductive. Specifically, none BP GO term in all species' analysis using module size of 30 (the most typically reported analysis in other publications). The wasp-focused analyses present not a single significant GO term, as expected by species-level WGCNA analyses. The bee-focused analyses list up to 49 BP GO terms (module size 30). 

Out of the 21 GO terms enriched in all species for either reproductives or non-reproductives, three notable terms associated with chromatin are present: regulation of chromatin assembly or disassembly, RSC-type complex, brahma complex. As a reminder, chromatin assembly is one important term found in the REVIGO analysis (Fig 3b) based on SVM and DEG genes. Katie and I think this is an notable, kind-of-interesting finding worth mentioning.





```{r record versions of session, eval = TRUE, echo = FALSE, include = FALSE}
# record versions of R and packages here
sessionInfo()
# R version 3.6.3 (2020-02-29)
# Platform: x86_64-apple-darwin15.6.0 (64-bit)
# Running under: macOS Catalina 10.15.4
# 
# Matrix products: default
# BLAS:   /System/Library/Frameworks/Accelerate.framework/Versions/A/Frameworks/vecLib.framework/Versions/A/libBLAS.dylib
# LAPACK: /Library/Frameworks/R.framework/Versions/3.6/Resources/lib/libRlapack.dylib
# 
# locale:
# [1] en_GB.UTF-8/en_GB.UTF-8/en_GB.UTF-8/C/en_GB.UTF-8/en_GB.UTF-8
# 
# attached base packages:
# [1] stats     graphics  grDevices utils     datasets  methods   base     
# 
# other attached packages:
# [1] forcats_0.5.0   stringr_1.4.0   dplyr_0.8.5     purrr_0.3.4     readr_1.3.1    
# [6] tidyr_1.0.3     tibble_3.0.1    tidyverse_1.3.0 ggplot2_3.3.0  
# loaded via a namespace (and not attached):
#  [1] Rcpp_1.0.4.6     cellranger_1.1.0 pillar_1.4.4     compiler_3.6.3   dbplyr_1.4.3    
#  [6] tools_3.6.3      lubridate_1.7.8  jsonlite_1.6.1   lifecycle_0.2.0  gtable_0.3.0    
# [11] nlme_3.1-147     lattice_0.20-41  pkgconfig_2.0.3  rlang_0.4.6      reprex_0.3.0    
# [16] cli_2.0.2        DBI_1.1.0        rstudioapi_0.11  yaml_2.2.1       haven_2.2.0     
# [21] xfun_0.13        xml2_1.3.2       withr_2.2.0      httr_1.4.1       knitr_1.28      
# [26] fs_1.4.1         generics_0.0.2   vctrs_0.3.0      hms_0.5.3        grid_3.6.3      
# [31] tidyselect_1.1.0 glue_1.4.1       R6_2.4.1         fansi_0.4.1      readxl_1.3.1    
# [36] modelr_0.1.7     magrittr_1.5     scales_1.1.1     backports_1.1.7  ellipsis_0.3.0  
# [41] rvest_0.3.5      assertthat_0.2.1 colorspace_1.4-1 stringi_1.4.6    munsell_0.5.0   
# [46] broom_0.5.6      crayon_1.3.4 
```
